\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}\usepackage{setspace} \usepackage{indentfirst}\usepackage{multicol}
\usepackage{verbatim} \usepackage{hyperref} \usepackage{fancyhdr}
\usepackage{etaremune} \usepackage{times} 
\pagestyle{fancy} \rhead{\emph{20 March 2026}} \renewcommand{\headrulewidth}{0pt}
\renewcommand{\bibitem}{\vskip2pt\par\hangindent\parindent\hskip-\parindent}




\begin {document} 
\begin{center}
%\LARGE{\textbf{Michael G. Findley}} \\ Frank C. Erwin, Jr. Centennial Professor of Government, \\ Business, and Public Affairs
\LARGE{\textbf{Michael G. Findley}} \\ Frank C. Erwin, Jr. Centennial Professor of Government 
\\ Professor of Business \& Public Affairs (by courtesy)

\end{center}

\section*{CONTACT INFORMATION}

\begin{multicols}{2}
\noindent 3.102 BAT, University of Texas at Austin  \\ 
Austin, TX 78712 \\ Phone: 512.749.3815
\begin{flushright} Email:
\texttt{mikefindley@utexas.edu}
\\ Website: \href{http://michael-findley.com}{http://michael-findley.com} \\ ORCID-ID: \texttt{0000-0002-4830-1828}
\end{flushright}
\end{multicols}


\section*{EDUCATION}
\noindent Ph.D. \textit{University of Illinois, Urbana-Champaign} (UIUC), Political Science (2007)

\noindent M.A., B.A. \textit{Utah State University} (USU), Political Science (2002, 2000)

\section*{APPOINTMENTS \& AFFILIATIONS}

\noindent  Frank C. Erwin, Jr. Centennial Professor of Government, \textit{UT Austin}, September 2021--present.

\noindent  Fellow at the Institute for Advanced Study in Toulouse (IAST), \textit{Toulouse School of Economics}, 2024--2025. %maybe it's here?: Universit\'e Toulouse Capitole

\noindent Professor (Courtesy), McCombs School of Business, \textit{UT Austin}.

\noindent Professor (Courtesy), LBJ School of Public Affairs, \textit{UT Austin}.

\noindent Merrill R. Merrill Endowed Visiting Chair, Department of Political Science, \textit{Utah State University}, 2024--2025. 

\noindent Provost's Teaching Fellow, \textit{UT  Austin}, September 2020--August 2024.

\noindent Co-Director and Co-Founder, Innovations for Peace and Development, \textit{UT Austin}, 2013--present.

\noindent Faculty Affiliate, \textit{Bernard and Audre Rapoport Center for Human Rights and Justice, UT Austin}, 2018--present.

\noindent Distinguished Scholar, \textit{Robert S. Strauss Center, Lyndon B. Johnson School, UT Austin}, 2012--present.

\noindent Professor, Associate Professor, Assistant Professor, Department of Government, \textit{UT Austin}, 2012--2021.


%\noindent Principal Investigator, \textit{AidData}, 2008--present

%\noindent AidData Conflict Mitigation Team Leader, \textit{AidData Research Consortium}, October 2013--September 2014

%\noindent Member, \textit{Evidence in Governance and Politics} Network, 2012-- (Steering Committee, 2012--2013)

\noindent Assistant Professor, Department of Political Science, \textit{Brigham Young University}, 2007--2012.

%\noindent Associate Director, \textit{Political Economy and Development Lab, BYU}, 2008--2012

%\noindent Guest Researcher, \textit{Uppsala Peace and Conflict Department, Sweden}, May 2010; June 2011



\section*{PUBLICATIONS}


\noindent \subsection*{Books}

\begin{etaremune}

\item Findley, Michael G., Michael Denly, and Kyosuke Kikuta. \textit{External Validity for Social Inquiry}. Cambridge, UK: Cambridge University Press. (Under Contract; Resubmitted)

\item Findley, Michael G., Daniel Nielson, and J.C. Sharman. 2014. \textit{Global Shell Games: Experiments in Transnational Relations, Crime, and Terrorism.} Cambridge, UK: Cambridge University Press. 

%Cambridge University Press ranked first among book publishers according to Garand and Giles 2011

\end{etaremune}


\noindent \subsection*{Journal Special Issues}

\begin{etaremune}

\item Findley, Michael, Nathan Jensen, Edmund Malesky, and Thomas Pepinsky (Co-editors). 2016. ``Research Transparency in the Social Sciences.'' Special Issue of \textit{Comparative Political Studies} 49(3): 1667--1815.

%*5 year ISI impact factor: 2.808 (11/161 in political science); Garand and Giles 8/92; Combes and Linnemer NA.

\item Hawkins, Darren G., J. Timmons Roberts, and Michael G. Findley (Co-editors). 2011. ``Expanding Our Understanding of Aid With a New Generation in Development Finance Information.'' Special Issue of \textit{World Development} 39(11): 1891--2054. 
%	\\ \indent -Rank-- ISI:  49 of 333 (I. Factor: 1.612); Garand/Giles: XX of 90; Combes \& Linnemer: 40 of 1168.

\end{etaremune}


\subsection*{Refereed Articles \& Law Reviews (Newest First) (*Student)}    

\begin{etaremune}

\item Findley, Michael G., Daniel L. Nielson. Forthcoming. ``A Natural Field Experiment on the Effectiveness of Economic Sanctions Before and After the Russian Invasion of Ukraine.'' \textit{Nature Human Behaviour}.

\item Callen, Michael, Miguel Fajardo-Steinh{\"a}user*, Michael G. Findley, and Tarek Ghani. 2025. ``Can Digital Aid Deliver in Humanitarian Crises?'' \textit{Management Science}. 71(11): 9730--9748.

\item Verrilli, Allison*, Marcel Roman, Hannah Walker, Derek Epp, Amy Liu, and Michael G. Findley. 2025. ``Policing Socio-Geographic Boundaries and Inequality.''  \textit{Perspectives on Politics}. 23(SI4): 1286--1306.

\item Findley, Michael G., Daniel L. Nielson, and J.C. Sharman. 2025. ``Banking Bad? A Global Field Experiment on Risk, Reward, and Regulation.'' \textit{American Journal of Political Science} 69(2): 545--559.

\item Findley, Michael G., Faten Ghosn, and Sara Lowe*. 2024. ``Vulnerability in Research Ethics: A Call for Assessing Vulnerability and Implementing Protections.'' \textit{Proceedings of the National Academy of Sciences} 121(34): 1--12. 

\item Aronson, Jacob, Michael G. Findley, Kyosuke Kikuta, and James Igoe Walsh. 2024. ``The Tyranny of Supply: Natural Resources and Rebel Territorial Control in Civil Conflicts.'' \textit{International Studies Quarterly} 68(3): 1--14.

\item Findley, Michael G., Daniel Strandow, Joseph K. Young, and Olgahan Cat*. 2023. ``Aiding War: How Foreign Aid Intensifies Armed Violence.'' \textit{International Studies Quarterly} 67(3): 1--15.

\item Liu, Amy H., Michael G. Findley, David Leal, Raul L. Madrid, Eric L. McDaniel, God'swill Osa*, Tasha Philpot, Brooke Shannon*, Zeynep Somer-Topcu, Chris Wlezien. 2023. ``Normalizing Diversity in Merit Review Forms.'' \textit{PS: Political Science and Politics} 56(1): 123--127.

\item Denly, Michael*, Michael Findley, Joelean Hall*, Andrew Stravers*, and James Walsh. 2022. ``Do Natural Resources Really Cause Conflict? Evidence From the New Global Resources Dataset.'' \textit{Journal of Conflict Resolution} 66(3): 387--412.

\item Findley, Michael G., Kyosuke Kikuta*, and Michael Denly*. 2021. ``External Validity.'' \textit{Annual Review of Political Science} 24: 365--393. 

\item Jensen, Nathan, Michael G. Findley, and Daniel L. Nielson. 2020. ``Electoral Institutions and Electoral Cycles in Investment Incentives: A Field Experiment on Over 3,000 U.S. Municipalities.'' \textit{American Journal of Political Science} 64(4): 807--822.

\item Marineau, Josiah*, and Michael G. Findley. 2020. ``The Swarm Principle: A Sub-national Spatial Analysis of Donor Coordination in Sub-Saharan Africa.'' \textit{Stability} 9(1): 1--22.

\item Marineau, Josiah*, Henry Pascoe*, Alex Braithwaite, Michael G. Findley, and Joseph K. Young. 2020. ``The Local Geography of Transnational Terrorist Attacks.'' \textit{Conflict Management and Peace Science} 37(3): 350--381.

\item Sexton, Renard, Rachel Wellhausen, and Michael G. Findley. 2019. ``How Government Reactions to Violence Worsen Social Welfare: Evidence from Peru.'' \textit{American Journal of Political Science} 63(2): 353--367.

\item White, Philip, Candace Berrett, Shannon Neeley, and Michael G. Findley. 2019. ``Modeling Efficiency of Foreign Aid Allocation in Malawi.'' \textit{The American Statistician} 73(4): 385--399.

\item Findley, Michael G. 2018. ``Does Foreign Aid Build Peace?'' \textit{Annual Review of Political Science} 21: 359--384.

\item Harris, Adam S.*, Michael G. Findley, Daniel L. Nielson, and Kennard L. Noyes*. 2018. ``The Economic Roots of Anti-Immigrant Prejudice in the Global South: Evidence from South Africa.'' \textit{Political Research Quarterly} 71(1): 228--241.

\item Findley, Michael G., Adam S. Harris*, Helen V. Milner, and Daniel L. Nielson. 2017. ``Who Controls Foreign Aid? Elite versus Public Perceptions of Donor Influence in Aid-Dependent Uganda.'' \textit{International Organization} 71(4): 633--663.

\item Findley, Michael G., Brock Laney*, Daniel L. Nielson, and J.C. Sharman. 2017. ``External Validity in Parallel Global Field and Survey Experiments on Anonymous Incorporation.'' \textit{Journal of Politics} 79(3): 856--872.

\item Findley, Michael G., Helen V. Milner, and Daniel L. Nielson. 2017. ``The Choice among Aid Donors: The Effects of Multilateral vs. Bilateral Aid on Recipient Behavioral Support.'' \textit{Review of International Organizations} 12(2): 307--334.

\item Campbell, Susanna, Michael G. Findley, and Kyosuke Kikuta*. 2017. ``An Ontology of Peace: Landscapes of Conflict and Cooperation.'' \textit{International Studies Review} 19(1): 92--113.

\item Allred, Brent B., Michael G. Findley, Daniel L. Nielson, J.C. Sharman. 2017. ``Anonymous Shell Companies: A Global Audit Study and Field Experiment in 176 Countries.'' \textit{Journal of International Business Studies} 48(5): 596--619.


\item Findley, Michael G., Nathan Jensen, Edmund Malesky, and Thomas Pepinsky. 2016. ``Can Results Free Review Reduce Publication Bias? The Results and Implications of a Pilot Study.'' \textit{Comparative Political Studies} 49(3): 1667--1703.


%*5 year ISI impact factor: 2.754 (14/161 in political science); Garand and Giles 3/92; Combes and Linnemer NA.

\item Tao, Ran, Daniel Strandow, Michael G. Findley, Jean-Claude Thill, and James I. Walsh. 2016. ``A Hybrid Approach to Modeling Territorial Control in Violent Armed Conflicts.'' \textit{Transactions in GIS} 20(3): 413--425.


\item Rudloff, Peter J., and Michael G. Findley. 2016. ``The Downstream Effects of Combatant Fragmentation on Civil War Recurrence.'' \textit{Journal of Peace Research} 53(1): 19--32.

%*5 year ISI impact factor: 3.549 (5/161 in political science; 4/85 in international relations); Garand and Giles 38/92; Combes and Linnemer 81/1168.

\item Asal, Victor, Michael G. Findley, James A. Piazza, and James Igoe Walsh. 2016. ``Political Exclusion, Oil, and Ethnic Armed Conflict.'' \textit{Journal of Conflict Resolution} 60(8): 1343--1367.
%	\\ \indent \textit{-International Studies Association Annual Meeting}, Toronto, March 2014

%*5 year ISI impact factor: 3.099 (6/161 in political science; 5/85 in international relations); Garand and Giles 10/92; Combes and Linnemer 39/1168.

\item Milner, Helen V., Daniel L. Nielson, and Michael G. Findley. 2016. ``Citizen Preferences and Public Goods: Comparing Preferences for Foreign Aid and Government Programs in Uganda.'' \textit{Review of International Organizations} 11(2): 219--245. 

%*5 year ISI impact factor: 1.698 (37/161 in political science; 14/85 in international relations); Garand and Giles NA; Combes and Linnemer 312/1168.


\item Chatterji, Aaron, Michael G. Findley, Nathan M. Jensen, Stephan Meier, and Daniel L. Nielson. 2016. ``Field Experiments in Strategy Research.'' \textit{Strategic Management Journal} 37(1): 116--132.

%*5 year ISI impact factor: 6.061 (7/115 in Business; 12/185 in Management); Garand and Giles NA; Combes and Linnemer NA.

\item Findley, Michael G., and Joseph K. Young. 2015. ``Terrorism, Spoiling, and the Resolution of Civil Wars.'' \textit{Journal of Politics}. 77(4): 1115--1128.

%*5 year ISI impact factor: 2.754 (14/161 in political science); Garand and Giles 3/92; Combes and Linnemer NA.


\item Findley, Michael G., and Josiah Marineau*. 2015. ``Lootable Resources and Third-Party Intervention Into Civil Wars.'' \textit{Conflict Management and Peace Science}. 32(5): 465-486.

%*5 year ISI impact factor: 1.426 (20/85 in international relations); Garand and Giles 76/92; Combes and Linnemer 199/1168.

\item Findley, Michael G., Daniel Nielson, and J.C. Sharman. 2015. ``The Causes of Non-Compliance with International Law: Evidence from a Field Experiment on Financial Transparency.'' \textit{American Journal of Political Science} 59(1): 146--161.

 %*5 year ISI impact factor: 4.506 (3/161 in political science); Garand and Giles 2/92; Combes and Linnemer NA.


\item Harris, Adam S.*, and Michael G. Findley. 2014. ``Is Ethnicity Identifiable? Lessons from an Experiment in South Africa.'' \textit{Journal of Conflict Resolution} 58(1): 4--33.

%*5 year ISI impact factor: 3.099 (6/161 in political science; 5/85 in international relations); Garand and Giles 10/92; Combes and Linnemer 39/1168.


\item Baradaran, Shima, Michael G. Findley, Daniel L. Nielson, and J.C. Sharman. 2014. ``Funding Terror.''  \textit{University of Pennsylvania Law Review}. 162(3): 477--536.

%*Washington and Lee Rankings: 5/1382


\item Milton, Daniel J., Megan Spencer*, and Michael G. Findley. 2013. ``Radicalism of the Hopeless: Refugee Flows and Transnational Terrorism.'' \textit{International Interactions} 39(5): 621-645.

%*5 year ISI impact factor: 1.245 (24/85 in international relations); Garand and Giles 87/92; Combes and Linnemer NA.


\item Findley, Michael G., Daniel Nielson, and J.C. Sharman. 2013. ``Using Field Experiments in International Relations: A Randomized Study of Anonymous Incorporation.'' \textit{International Organization} 67(4): 657--693. 

%*5 year ISI impact factor: 4.922 (1/85 in international relations); Garand and Giles 5/92; Combes and Linnemer 22/1168.


\item Findley, Michael G. 2013. ``Bargaining and the Interdependent Stages of Civil War Resolution.'' \textit{Journal of Conflict Resolution.} 57(5): 901--928.

%*5 year ISI impact factor: 3.099 (6/161 in political science; 5/85 in international relations); Garand and Giles 10/92; Combes and Linnemer 39/1168.

\item Baradaran, Shima, Michael G. Findley, Daniel L. Nielson, and J.C. Sharman. 2013. ``Does International Law Matter?'' \textit{Minnesota Law Review} 97(3): 743--837. 
% 	\\ \indent -Rank-- Washington \& Lee: Ranked 11th of 1382 Journals Overall


\item Findley, Michael G., and Joseph K. Young. 2012.  ``Terrorism and Civil War: A Spatial and Temporal Approach to a Conceptual Problem.'' \textit{Perspectives on Politics} 10(2): 285--305.

%*5 year ISI impact factor: 2.661 (16/161 in political science); Garand and Giles 11/92; Combes and Linnemer XX/1168.

%*Translated into Russian for edited volume \textit{Contemporary Foreign International Relations Studies.} Russian International Affairs Council.

\item Findley, Michael G., and Peter J. Rudloff. 2012. ``Combatant Fragmentation and the Dynamics of Civil Wars.'' \textit{British Journal of Political Science} 42(4): 879--901.

%*5 year ISI impact factor: 2.775 (13/161 in political science); Garand and Giles 4/92; Combes and Linnemer NA.

\item Findley, Michael G., and Joseph K. Young. 2012. ``More Combatant Groups, More Terror? Empirical Tests of an Outbidding Logic.'' \textit{Terrorism and Political Violence} 24(5): 706--721.

%*5 year ISI impact factor: 0.863 (81/161 in political science); Garand and Giles NA; Combes and Linnemer NA.

\item Findley, Michael G., and Joseph K. Young. 2012. ``Using Geography to Understand Terrorist Actors and Actions.'' \textit{International Studies Review.} Appears in an ISR Forum entitled ``Killing Civilians or Holding Territory? How to Think About Terrorism'' (edited by Victor Asal, Luis De La Calle Robles, Michael Findley, and Joseph Young). 14(3): 475--497.

%*5 year ISI impact factor: 1.177 (63/161 in political science); Garand and Giles NA; Combes and Linnemer NA.


\item Findley, Michael G., James Piazza, and Joseph K. Young. 2012. ``Games Rivals Play: Terrorism in International Rivalries.'' \textit{Journal of Politics}. 74(1): 235--248. 

%*5 year ISI impact factor: 2.754 (14/161 in political science); Garand and Giles 3/92; Combes and Linnemer NA.

\item Young, Joseph K., and Michael G. Findley. 2011. ``Can Peace Be Purchased? A Sectoral-Level Analysis of Aid's Influence on Transnational Terrorism'' \textit{Public Choice} 149(3-4): 365--381. 

%*5 year ISI impact factor: 1.218 (61/161 in political science); Garand and Giles 35/92; Combes and Linnemer 80 of 1168.


\item Findley, Michael G., Josh Powell*, Daniel Strandow, and Jeff Tanner*. 2011. ``The Localized Geography of Foreign Aid: A New Dataset and Application to Violent Armed Conflict.'' \textit{World Development} 39(11): 1995--2009.
%	\\ \indent -Rank-- ISI:  49 of 333 (I. Factor: 1.612); Garand/Giles: XX of 90; Combes \& Linnemer: 40 of 1168.

\item Tierney, Michael J., Daniel L. Nielson, Darren G. Hawkins, J. Timmons Roberts, Michael G. Findley, Ryan M. Powers, Bradley Parks, Sven E. Wilson, Robert L. Hicks. 2011. ``More Dollars Than Sense: Refining Our Knowledge of Development Finance Using AidData.'' \textit{World Development} 39(11): 1891--1906. 
%	\\ \indent -Rank-- ISI:  49 of 333 (I. Factor: 1.612); Garand/Giles: XX of 90; Combes \& Linnemer: 40 of 1168.

\item Young, Joseph K., and Michael G. Findley. 2011. ``Promise and Pitfalls of Terrorism Research.'' \textit{International Studies Review}. 13(3): 411--431. 
%*5 year ISI impact factor: 1.177 (63/161 in political science); Garand and Giles NA; Combes and Linnemer NA.


\item Findley, Michael G., and Joseph K. Young. 2011. ``Terrorism, Democracy, and Credible Commitments.'' \textit{International Studies Quarterly}. 55 (2): 357--378. 

%*5 year ISI impact factor: 2.189 (24/161 in political science); Garand and Giles 9/92; Combes and Linnemer NA.


\item Nielsen, Richard A., Michael G. Findley, Zachary S. Davis*, Tara Candland*, and Daniel L. Nielson. 2011. ``Foreign Aid Shocks as a Cause of Violent Armed Conflict.'' \textit{American Journal of Political Science}. 55(2): 219--232.  

%*5 year ISI impact factor: 4.506 (3/161 in political science); Garand and Giles 2/92; Combes and Linnemer NA.


\item  Rider, Toby J., Michael G. Findley, and Paul F. Diehl. 2011. ``Just Part of the Game?: Arms Races, Rivalry, and Competition.'' \textit{Journal of Peace Research} 48(1): 85--100. 

%*5 year ISI impact factor: 3.549 (5/161 in political science; 4/85 in international relations); Garand and Giles 38/92; Combes and Linnemer 81/1168.

\item Bhavnani, Ravi, Michael G. Findley, and James H. Kuklinski. 2009. ``Rumor Dynamics in Ethnic Violence.'' \textit{Journal of Politics} 71(3): 876--892. 

%*5 year ISI impact factor: 2.754 (14/161 in political science); Garand and Giles 3/92; Combes and Linnemer NA.


\item Findley, Michael G. 2008. ``Agents and Conflict: Adaptation and the Complexity of War.'' \textit{Complexity} 14(1): 22--35. 

%*5 year ISI impact factor: 1.342 (40/99 in Math Interdisciplinary applications); Garand and Giles NA; Combes and Linnemer NA.

\item Findley, Michael G., and Joseph K. Young. 2007. ``Fighting Fire with Fire?: How (Not) to Neutralize an Insurgency.'' \textit{Civil Wars} 9(4): 378--401. 
%	\\ \indent -Not Ranked in ISI or Garand/Giles.

\item Findley, Michael G., and Scott Edwards. 2007. ``Accounting for the Unaccounted: Weak-Actor Social Structure in Asymmetric Wars.'' \textit{International Studies Quarterly} 51(3): 583--606. 

%*5 year ISI impact factor: 2.189 (24/161 in political science); Garand and Giles 9/92; Combes and Linnemer NA.


\item Findley, Michael G., and Tze Kwang Teo. 2006. ``Rethinking Third Party Interventions into Civil Wars: An Actor-Centric Approach.'' \textit{Journal of Politics} 68(4): 828--837. 

%*5 year ISI impact factor: 2.754 (14/161 in political science); Garand and Giles 3/92; Combes and Linnemer NA.

\end{etaremune}



\subsection*{Selected Policy Publications}    %\& Presentations

\begin{etaremune}

\item Findley, Michael G., Daniel L. Nielson, and J.C. Sharman. 2021. ``Anti-Corruption Measures.'' Invited Paper for the \textit{UN High Level Panel on Financial Accountability, Transparency, and Integrity.} United Nations.

\item Findley, Michael G., Oliver Kaplan, Joseph K. Young, Ana Marrugo, Alejandro Ponce de Leon, and Daniel Walker. 2021. ``Endline Report: Regional Governance in Colombia: Results from an Impact Evaluation.'' USAID Colombia Mission. 

\item Findley, Michael G., Daniel Sabet, and Aleta Starosta. 2021. ``DRG Impact Evaluation Retrospective: Learning from Three Generations of Impact Evaluations.'' \textit{USAID DRG Center and Cloudburst}.

\item Denly, Michael, Michael G. Findley, John Gerring, and Rachel Wellhausen. 2019. ``Governance in Armenia: An Evidence Review for Learning and, Evaluation and Research Activity II (LER II).'' \textit{USAID DRG Center and Cloudburst.}

\item Denly, Michael, Michael G. Findley, Vepa Rejepov, and Rachel Wellhausen. 2019. ``Integrity Systems and the Rule of Law in Armenia: An Evidence Review for Learning and, Evaluation and Research Activity II (LER II).'' \textit{USAID DRG Center and Cloudburst.}

\item Kahler, Miles, Maya Forstater, Michael G. Findley, Jodi Vittori, Erica Westenberg, and Yaya J. Fanusie. 2018. ``Global Governance to Combat Illicit Financial Flows: Measurement, Evaluation,  Innovation.'' \textit{Council on Foreign Relations.} 

\item Arias, Viviana, Cesar Caballero, Michael G. Findley, Oliver Kaplan, Ana Marrugo, William Matthias, Alejandro Ponce de Leon, Maria Paula Rojas, Angelika Rettberg, Michael Weintraub, and Joseph K. Young. 2018. ``Data4Peace.'' \textit{Documentos de Trabajo: Escuela de Gobierno Alberto Llera Camargo} 47. 

\item Findley, Michael G., Oliver Kaplan, Joseph K. Young, Ana Marrugo, Alejandro Ponce de Leon, and Daniel Walker. 2018. ``Midline Report: Regional Governance in Colombia: Results from an Impact Evaluation.'' USAID Colombia Mission. 

\item Jensen, Nathan M., Michael G. Findley, and Daniel L. Nielson. 2016. ``Electoral Institutions and Electoral Cycles in Foreign Direct Investment: A Field Experiment on Over 3,000 U.S. Municipalities." \textit{Washington Center for Equitable Growth} Working Paper Series. Accessed \href{http://equitablegrowth.org/electoral-institutions-and-electoral-cycles-in-foreign-direct-investment/}{here}. 

\item Findley, Michael G., Oliver Kaplan, Joseph K. Young, Ana Marrugo, Alejandro Ponce de Leon, and Daniel Walker. 2016. ``Baseline Report: Regional Governance in Colombia: Results from an Impact Evaluation.'' USAID Colombia Mission. 

\item Campbell, Susanna, Tracy Dexter, Michael Findley, Stephanie Hofmann, Josiah Marineau, and Daniel Walker. 2015. ``Independent External Evaluation UN Peacebuilding Fund Project Portfolio in Burundi 2007--2013.'' \textit{United Nations Peacebuilding Support Office.} 

\item Weaver, Catherine, Stephen Davenport, Justin Baker*, Michael Findley, Christian Peratsakis, and Josh Powell. 2014. ``Malawi's Open Aid Map.'' World Bank.

\item Campbell, Susanna P., Michael G. Findley, and Jennifer Welch. 2014. ``White Paper:  Learning and Evaluation in Technology and Peacebuilding.'' \textit{Build Peace.}

\end{etaremune}

\subsection*{Other Academic Publications}    %\& Presentations

\begin{etaremune}

\item Findley, Michael G., and Joseph K. Young. 2020. ``The Weakest Link: Scholarship and Policy on Intrastate Conflict.'' Prepared for Edited Volume \textit{Bridging the Theory-Practice Divide in International Relations.} Georgetown University Press. (Editors Danial Maliniak, Susan Peterson, Ryan Powers, and Michael Tierney)  [Editor reviewed]

\item Farrell, Megan*, Michael G Findley, and Joseph K. Young. 2019. ``Geographic Approaches in the Study of Terrorism.'' In Erica Chenoweth, Richard English, Andreas Gofas, Stathis Kalyvas (Eds.) \textit{Oxford Handbook of Terrorism}.

\item Findley, Michael G., and Daniel L. Nielson. 2016. ``Obligated to Deceive? Aliases, Confederates, and the Common Rule in International Field Experiments.'' In Scott Desposato (Ed.) ``Ethics and Experiments: Problems and Solutions for Social Scientists.'' \textit{Routledge Experiments in Political Science Series}.

\item Strandow, Daniel, Michael G. Findley, and Joseph K. Young. 2016. ``Foreign Aid and Territorial Control in Civil War: A GIS Approach.'' \textit{AidData Working Paper \#24}. Williamsburg, VA: AidData. Accessed \href{http://docs.aiddata.org/ad4/pdfs/wps24_foreign_aid_and_the_intensity_of_violent_armed_conflict.pdf}{here}.

\item Findley, Michael G., Daniel Nielson, and J.C. Sharman. 2015. "Orchestrating the Fight Against Anonymous Incorporation: A Field Experiment.'' In Kenneth Abbott, Phillip Genschel, Duncan Snidal and Bernhard Zangl (Eds.)  \textit{International Organizations as Orchestrators}. Cambridge, UK: Cambridge University Press. (Peer-reviewed)

\item Campbell, Susanna, Josiah Marineau*, Tracy Dexter, Michael Findley, Stephanie Hofmann, and Daniel Walker*. 2015. ``Peacebuilding in Burundi and the Impact of the UN Peacebuilding Fund Portfolio, 2007--2013.'' In Cedric de Coning and Eli Stamnes (Eds.) \textit{The 2015 Review of the UN's Peacebuilding Architecture: Impact of the first 10 years?}. 

\item Findley, Michael G., Adam S. Harris, Helen V. Milner and Daniel Nielson. 2015. ``Elite and Mass Support for Foreign Aid Versus Government Programs: Experimental Evidence from Uganda.'' \textit{AidData Working Paper \#23}. Williamsburg, VA: AidData. Accessed \href{http://aiddata.org/aiddata-working-paper-series}{here}.

\item Young, Joseph, and Michael G. Findley. 2014. ``Computational Modeling to Study Conflicts and Terrorism.'' In Joseph Soeters, Patricia M. Shields, and Sebastiaan Rietjens (Eds.)  \textit{Handbook of Research Methods in the Military.} 249--260.   

\item Kitterman, Katherine*, and Michael G. Findley. 2014. ``Emerging Donors and the Changing Landscape of Bilateral Aid.'' In Manuela Moschella and Catherine Weaver (Eds.)  \textit{Handbook of Global Economic Governance.} Routledge.

\item Blaschke, Sean M., Peter P. Carroll, Daniela Rojas Chaves, Michael G. Findley, Madeleine C. Gleave, Robert N. Morello, and Daniel L. Nielson. 2014. ``Extrinsic, Intrinsic, and Social Incentives for Crowdsourcing Development Information in Uganda: A Field Experiment.'' \textit{The United Nations Children's Fund.}

\item Findley, Michael, Macartan Humphreys, and Jeremy Weinstein. 2012. ``Proposal for a Pilot Registry for Political Science (PREPS).'' Presented to editors of the \textit{American Political Science Review}, \textit{American Journal of Political Science}, \textit{Journal of Politics}, \textit{Political Analysis}, and \textit{Quarterly Journal of Political Science}.

\item Strandow, Daniel, Michael Findley, Daniel Nielson, and Josh Powell. 2011. ``The UCDP and AidData Codebook on Geo-Referencing Aid, Version 1.1'' \textit{UCDP Paper No. 4.}

\end{etaremune}


\section*{RESEARCH IN PROGRESS}


\subsection*{Under Review or Completed \& Submitting Soon}

\begin{etaremune}\setlength{\itemsep}{3pt}

\item ``Employing Ex-combatants: A Resume Experiment in Colombia.'' (With Oliver Kaplan) Registered report under review at \textit{Nature}.

\item \textit{Aid in Conflict: Donor Behavior in Conflict Affected Countries.} Book manuscript. (With Susanna Campbell and Haley Swedlund.) Submitting to \textit{Oxford University Press} March 2026. 

\item ``The Strategic Logic of Targeting of Aid by Rebel Groups During War.'' With Trey Billing,  David Backer, and Jiseon Chang. Submitting March 2026.

\item ``Ex-combatant Demobilization and Support for Peace: A Reconciliation Quasi-Experiment in Colombia.'' (With Oliver Kaplan and Joseph K. Young.) Submitting March 2026.

\item ``Digital vs. Physical Cash in Humanitarian Assistance: Evidence from Pakistan.'' (With Miguel Fajardo-Steinh{\"a}user*)

\item ``Incorporation and Banking in Guineastan: Generalizability, Transportability, and Research Synthesis'' (With Daniel L. Nielson and J.C. Sharman)
 
\item ``Experimental Evidence from Uganda, South Africa, and the United States on Ethnic Identification and Ethnic Deception.'' With James Habyarimana, Adam Harris, Macartan Humphreys, Daniel Nielson, Daniel Posner, and Jeremy Weinstein. 

% \item ``Researcher Characteristics Strongly Affect Prosocial Helping in Field Experimentation.'' With Peter Carroll, Elizabeth McGuire, Catie Nielson, Brock Laney, Matthew Brigham, Madeleine Gleave, and Daniel Nielson. 

% \item ``Openness to Learning Among Non-State Actors: Two Global Field Experiments Encouraging NGOs to Update.'' With Eliza Riley Oak, Daniel L. Nielson, and James Hodgson.

% \item ``Using Field Experiments in International Business Research: Pricing Risk in Creating Anonymous Shell Corporations.'' With Brent Allred, Daniel Nielson, and J.C. Sharman.

\end{etaremune}


\noindent \subsection*{Work in Progress}

\begin{etaremune}\setlength{\itemsep}{3pt}

\item ``Leaders, Factions, and Political Violence: Evidence from China's Cultural Revolution.'' (With Xin Nong)

\item \textit{Banking Bad: How Criminals Hack Global Finance.} (With Daniel L. Nielson and J.C. Sharman.

\item \textit{Wrong is Right: How Experts Can Learn Better from Error.} (With Daniel L. Nielson)

\item ``Do Aid Shocks Cause Violent Conflict? Evidence from the Global Retrenchment of U.S. Foreign Assistance.'' (With Kylie Smith, ChangHa Kim, and Others)

\item ``Short-term Gains and Long-term Losses in International Peacebuilding.'' (With Danny Cowser and Renard Sexton.)


%\item ``Local Governance and Violence in Colombia: Evidence from a Thousand Interviews with Government Elites and a 10-year Panel Survey of National Leaders.'' (With Joe Young, Ollie Kaplan, and C\'{e}sar Caballero) [Research in progress]

%\item ``Modeling Territorial Control in Civil Wars: A New Dataset and Network-based Geospatial Analysis.'' (With Jacob Aronson, Kyosuke Kikuta, Ran Tao, Jean-Claude Thill, Jim Walsh) [Dataset and modeling complete; Paper in progress]

%\item ``Evaluation-Driven Adaptive Programming.'' (With Daniel Sabet and Aleta Starosta) [Research in progress]



\end{etaremune}



\section*{SELECTED MEDIA WRITING/COVERAGE}


\begin{etaremune}
\item \textit{VoxDev.} ``Can digital humanitarian aid reach vulnerable populations in fragile states?'' 19 Sep 2024. \href{https://voxdev.org/topic/finance/can-digital-humanitarian-aid-reach-vulnerable-populations-fragile-states}{[Link here.]}
\item \textit{International Consortium of Investigative Journalists.} ``Researchers took shell companies on a global shopping trip.'' 1 Dec 2021. (Coverage)
\item \textit{The Economist.} ``The shell games go on.'' 16 Oct 2021. (Coverage)
\item \textit{The New York Times.} ``Why we should preserve international institutions and order.'' 23 July 2018. (Co-Author)
\item \textit{Austin-American Statesman \& FACT Coalition.} ``Shell Companies Undermine Sanctions Against North Korea.'' 28 August 2017. (Co-Author)
\item \textit{Prospect Magazine.} ``London: the money laundering capital of the world.'' 27 April 2017. (Coverage)
\item \textit{The Economist.} ``How to crack a shell.'' 7 May 2016. (Coverage)
\item \textit{The New Republic.} ``U.S. Shell Companies Are Just as Common as Panamanian Ones.'' 12 April 2016. (Co-author)
\item \textit{The Conversation.} ``Panama Papers show how easy it is to finance terror using U.S. shell companies.'' (Co-author)
\item \textit{The Monkey Cage, Washington Post.} ``For research, we pretended to be crooks and terrorists and tried to buy shell companies. The results were disturbing.'' 7 April 2016. (Co-author)
\item \textit{CBS 60 Minutes.} ``Anonymous, Inc.'' 31 Jan 2016. (Coverage)
\item \textit{The New York Times.} ``Delaware, Den of Thieves?'' 1 Nov 2013. (Coverage)
\item \textit{The Economist.} ``Special report on offshore finance.'' 14 Feb 2013. (Coverage)
\item \textit{The Economist.} ``Launderers Anonymous.'' 22 Sep 2012. (Coverage)
\item \textit{NPR Planet Money.} ``We Set Up An Offshore Company In a Tax Haven.'' 27 Jul 2012. (Coverage)
\item \textit{Wall Street Journal.} ``Week in Ideas: Aid Shocks as a Cause of Conflict.'' 2 Oct 2010. (Coverage)
\item Other coverage: \textit{US Senate}, \textit{UK Government}, \textit{TED}, \textit{Global Witness}, \textit{Open Aid Partnership}, \textit{International Aid Transparency Initiative}, \textit{World Bank}, \textit{African Development Bank}, \textit{ONE Foundation}, \textit{Global Financial Integrity}, \textit{UK Channel 4}, \textit{Financial Transparency Coalition}, \textit{The Century Foundation}, \textit{Center for Effective Government}, \textit{Citizens for Tax Justice}, \textit{Financial Times}, \textit{Thomson-Reuters}, \textit{Devex}, \textit{The Hill}, \textit{The Guardian}, \textit{This is Africa Online}, \textit{The East African}, \textit{The African Economist}, \textit{International Bar Association}, \textit{FCPA Blog}, \textit{Democratic Underground}, \textit{Open Society}, \textit{La Tribuna}, \textit{lamarea}, \textit{Austin American Statesman}, \textit{Dallas Morning News}
\end{etaremune}



\section*{INVITED TALKS}

\singlespacing
\begin{etaremune}
\item\textit{-Registered Reports in IPE and Global Governance, Maastrict University Brussels Hub}, June 2026
\item\textit{-Tulane University, Department of Political Science}, April 2026
\item\textit{-Texas A\&M, Bush School}, March 2026
\item\textit{-Northwestern University, Department of Political Science}, February 2026
\item\textit{-University of Iowa, Department of Political Science}, November 2025
\item\textit{-Grants Workshop, UT Austin}, February 2026
\item\textit{-Institute for Advanced Study (IAST), Toulouse School of Economics}, June 2025
\item\textit{-Behavioural Insights Team, London, UK}, May 2025
\item\textit{-Diplomacy \& World Affairs, Occidental College}, April 2025 (Declined;  unavailable)
\item\textit{-CHASS Tanner Talk Series, Utah State University (2 of 2)}, April 2025
\item\textit{-The Suspension of U.S. Foreign Aid and the Future of International Development, Penn Development Research Initiative}, March 2025 (Declined; unavailable) 
\item\textit{-CHASS Tanner Talk Series, Utah State University (1 of 2)}, February 2025
\item\textit{-International Relations Seminar, UCSD}, Fall 2024 (Declined;  unavailable)
\item\textit{-National Ground Intelligence Center (NGIC), U.S. Army}, May 2024 (Declined;  unavailable)
\item\textit{-Behavioural Insights Team, London, UK}, April 2024
\item\textit{-Bush School of Public Affairs, Texas A\&M University}, April 2024
\item\textit{-Washington University in St. Louis, Department of Political Science}, April 2024 
\item\textit{-Meta-Research Innovation Center at Stanford (METRICS)}, September 2023 
\item\textit{-Lisbon School of Economics and Management, Lisbon, Portugal}, May 2023
\item\textit{-Institute for Advanced Study, Toulouse, France}, April 2023
\item\textit{-Central Bank of the Bahamas, Nassau, Bahamas}, January 2023
\item\textit{-Wolfsberg Group (Association of 13 global banks developing AML industry standards)}, November 2022
\item\textit{-University of Pennsylvania, Identity and Conflict Lab}, April 2022 
\item\textit{-Emory University, Political Science Department}, April 2022 
\item\textit{-Central Bank of the Bahamas, Nassau, Bahamas}, January 2022
\item\textit{-Empirical Implications of Theoretical Models}, Summer 2021 (Declined;  unavailable)
\item\textit{-USAID Center for Democracy, Human Rights, and Governance}, March 2021
\item\textit{-Hobby School of Public Affairs, University of Houston}, February 2021
\item\textit{-Department of Government, Dartmouth College}, February 2021 
\item\textit{-Central Bank of the Bahamas, Nassau, Bahamas}, January 2021
\item\textit{-RAND Corporation}, January 2021 (Virtual due to COVID-19)
\item\textit{-ESAN Organization of Central Texas (EOCT; Nigerian Socio-Cultural Association), November 2020} (Virtual Due to COVID-19
\item\textit{-ITESO University, Guadalajara}, May 2020 (Postponed due to COVID-19)
\item\textit{-Emory University, 2020 Human Rights Workshop}, April 2020  (Rescheduled due to COVID-19)
\item\textit{-Liberal Arts Refugee Alliance, University of Texas at Austin}, April 2020
\item\textit{-Notre Dame University, Kroc-Kellogg Institute}, February 2020
\item\textit{-Central Bank of the Bahamas, Nassau, Bahamas}, January 2020
\item\textit{-U.S. Agency for International Development Colombia Mission, Bogota Colombia}, January 2020
\item\textit{-University of Cambridge, Department of Politics and International Studies}, November 2019
\item\textit{-University College London, Department of Political Science}, November 2019.
\item\textit{-University of Oxford, Nuffield College International Relations}, November 2019.
\item\textit{-University of Oxford, Department of Politics and International Relations}, November 2019.
\item\textit{-Utah State University, Department of Political Science}, Oct 2019.
\item\textit{-Texas A\&M Department of Political Science, College Station, TX}, Sept 2019. 
\item\textit{-College of William \& Marcy, Global Research Institute}, June 2019.
%\item\textit{-University of Pennsylvania IR speaker series}, AY 2019--2020 TBA
\item\textit{-Utah State University Huntsman School of Business, Logan, UT}, Feb 2019
\item\textit{-University of North Texas Department of Political Science, Denton, TX}, Feb 2019
\item\textit{-Penn State University Department of Political Science, State College, PA}, Feb 2019
\item\textit{-United States Institute of Peace, Washington DC}, October 2018
\item \textit{-University of Southern California, CIS, Los Angeles}, September 2018
\item\textit{-U.S. Agency for International Development Colombia Mission, Bogota Colombia}, July 2018
\item \textit{-University of California, San Diego, San Diego, CA}, May 2018
\item \textit{-University of Texas at Austin Department of Geography and the Environment, Austin, TX}, April 2018
\item \textit{-College of William and Mary, Whole of Government National Security Conference}, April 2018
\item \textit{-University of Chicago Harris School, Chicago, IL}, March 2018
\item \textit{-University of Denver Korbel School, Denver, CO}, January 2018
\item \textit{-University of Texas at Austin White Rose Society Chapter, Austin, TX}, November 2017
\item \textit{-Center for International Studies (CIS) at University of Southern California, Los Angeles, CA}, November 2017
\item \textit{-U.S. Agency for International Development and AidData Workshop on Pioneering Development Research Using Geospatial Data, Washington D.C.}, October 2017
\item\textit{-University of California at Berkeley, Department of Political Science, Berkeley, CA}, April 2017.
\item\textit{-University of Illinois, Urbana-Champaign Political Science, Urbana, IL}, March 2017
\item \textit{-Massachusetts Institute of Technology, Department of Political Science, Cambridge, MA}, February 2017
\item\textit{-United States Agency for International Development, Washington DC}, December 2016
\item\textit{-United States Agency for International Development Kenya Mission, Nairobi Kenya}, October 2016
\item\textit{-University of Colorado at Boulder, Institute of Behavioral Science, Boulder, CO}, October 2016.
\item\textit{-U.S. Agency for International Development Colombia Mission, Bogota Colombia}, July 2016
\item\textit{-University of Texas at Dallas, Workshop on Political Violence, Dallas, TX}, May 2016
\item\textit{-US Department of State, Countering Violent Extremism \& Experimental Research Briefing, Washington, D.C.}, January 2016
\item\textit{-University of California at Berkeley, Berkeley Institute for Transparency in the Social Sciences Meeting}, December 2015
\item\textit{-UK Department for International Development, Sustainable Development Goals Briefing, United Kingdom}, December 2015
\item\textit{-University of California at Berkeley, Violence: Electoral Conflict in Comparative Perspective, Berkeley, CA (Declined)}, December 2015
\item\textit{-United States Agency for International Development Regional Governance Activity Impact Evaluation Methods, Bogota, Colombia}, August 2015
\item\textit{-University of Pittsburgh Political Science and Public Policy Speaker Series, Pittsburgh, PA}, April 2015
\item\textit{-Yale University Department of Political Science, New Haven, CT}, March 2015
\item\textit{-SFB 700 --- AidData Research Workshop, Berlin, Germany}, February 2015
\item\textit{-Strengthening the Links Scholarship and Policy Symposium, Williamsburg VA}, Jan 2015
\item\textit{-University of Texas Government Department Methods Symposium, Austin TX}, Oct 2014
\item\textit{-GeoCenter \& Monitoring and Evaluation Unit, United States Agency for International Development, Washington D.C.}, May 2014
\item\textit{-Office of Transition Initiatives, United States Agency for International Development, Washington D.C.}, May 2014
\item\textit{-Global Financial Integrity, Washington D.C.}, May 2014
\item\textit{-United Nations, United Nations Peacebuilding Fund, New York City, NY}, March 2014
\item\textit{-AidData Research Consortium Annual Convening, Williamsburg, VA}, January 2014
\item\textit{-Integrating Conflict Data, University of Maryland, College Park}, January 2014
\item\textit{-International Law and Regulation Lab, University of California, San Diego}, November 2013
\item\textit{-Center for the Study of Development Strategies, Columbia University}, November 2013
\item\textit{-Uppsala Workshop on Geography and Armed Conflict, Uppsala, Sweden}, October 2013
\item\textit{-United Nations Development Program M\&E for ICT}, Nairobi, Kenya, October 2013
\item\textit{-Texas A\&M Conflict and Development Lab, College Station, TX}, October 2013
\item\textit{-Roundtable on Ethics in Comparative Politics Experiments, APSA, Chicago}, August 2013
\item\textit{-Conference on Ethics in Comparative Politics Experiments, UC San Diego}, May 2013
\item\textit{-Invited workshop on Foreign Aid, Princeton University, Princeton, NJ}, April 2013
\item\textit{-Roundtable on Innovative Research on Non-Governmental Organizations, MPSA, Chicago}, April 2013
\item\textit{-Shifting Conflict Patterns in Africa: Drivers of Instability and Strategies of Cooperation, University of Texas, Austin}, April 2013
\item\textit{-Transforming Security Research Workshop, Washington, D.C.}, February 2013 (declined)
\item\textit{-Department of Political Science, Oklahoma State University, Stillwater, OK}, March 2013
\item\textit{-Wheatley Institution for International Affairs Conference, Provo, UT}, February 2013
\item\textit{-African Studies Academy, University of North Carolina, Charlotte}, February 2013
\item\textit{-Department of Political Science, University of Illinois, Urbana-Champaign}, October 2012
\item\textit{-NGO Toolkit for Conflict / Crisis Response}, South by Southwest (SXSW) Eco, October 2012
\item\textit{-Experimental Research Workshop, Best Practices and Applications, Princeton University, Princeton, NJ}, September 2012
\item\textit{-Field Experiments in International Relations, BYU and Princeton University, Park City, UT}, September 2012
\item\textit{-3ie Registry for International Development Impact Evaluations Task Force, RAND Corporation, Washington D.C.}, September 2012
\item\textit{-Tools of International Pressure: How International Actors Influence Domestic Politics in Sovereign States, Yale University, New Haven, CT}, June 2012
\item\textit{-Orchestration in International Relations Workshop, Ludwig-Maximilians University, Munich, Germany}, May 2012
\item\textit{-Evolving Dynamics of Security in Africa: Assessing Diplomacy, Development, and Defense Responses, University of Texas, Austin}, April 2012
\item\textit{-Roundtable on Innovative Uses of Geocoded Data in Political Science, MPSA, Chicago}, April 2012
\item\textit{-World Bank Mapping for Results Research Conference, Washington D.C.}, March 2012 (declined)
\item\textit{-Terrorism and the Resolution of Civil Wars, University of Texas, Austin}, March 2012
\item\textit{-Development Gateway Aid Management Platform Workshop, Dakar, Senegal}, January 2012
\item\textit{-Department of Statistics, Brigham Young University, Provo, UT}, January 2012
\item\textit{-AidData 2.0 launch and CCAPS Workshop on Climate Change, Development Gateway and World Bank}, November 2011
\item\textit{-Tech@State, State Department Conference on Data Visualization for International Development, Washington D.C.}, September 2011
\item\textit{-ESRI International User Conference, San Diego, CA} July 2011
\item\textit{-Mapping Climate Change and Political Stability, Austin, TX}, May 2011 (Declined due to research travel)
\item\textit{-Terrorism and Policy Conference, University of Texas, Dallas,} May 2011 %Sandler
\item\textit{-Development Gateway Aid Management Platform Workshop, Nairobi, Kenya}, December 2010
\item\textit{-Lyndon B. Johnson School of International Affairs, CCAPS, University of Texas, Austin}, November 2010
\item\textit{-World Bank, Mapping for Results, World Bank, Washington D.C.}, October 2010
\item\textit{-U.S. Department of State, Development Information and Mapping Summit, State Department, Washington D.C.}, October 2010
\item \textit{-History Alliance Seminar, Weber State University, Ogden, UT}, September 2010
\item \textit{-Department of Peace and Conflict Research, Uppsala University}, May 2010
\item \textit{-Uppsala Forum on Peace, Democracy, and Justice, Uppsala University} May 2010
\item \textit{-National Research Council, National Geospatial-Intelligence Agency Workshop}, May 2010 (declined)
\item \textit{-World Bank Conflict and Fragility Innovation Fair, Cape Town, SA}, April 2010
\item \textit{-Frank Church Symposium, Idaho State University}, March 2010
\item \textit{-Department of Political Science, College of William \& Mary}, December 2008
\item \textit{-Department of Political Science, Oklahoma State University}, June 2008
\item \textit{-Department of Political Science, University of Illinois, Urbana-Champaign}, May 2008
\item \textit{-Complex Systems Symposium, Department of Physics, University of Illinois, Urbana-Champaign}, May 2006
\item \textit{-New Faces in Security Studies, Triangle Institute for Security Studies, Duke}, September 2006
\end{etaremune}


\section*{CONFERENCE PRESENTATIONS (BY PAPER)}

\begin{itemize}

\item ``Leaders, Factions, and Political Violence: Evidence from China's Cultural Revolution.'' 
\\ \indent \textit{-Peace Science Society Annual Meeting}, Ann Arbor, MI, November 2024.

\item ``Can Digital Aid Deliver in Humanitarian Crises?'' 
\\ \indent \textit{-Innovations for Poverty Action Annual Meeting, Northwestern University}, Evanston, IL, October 2023.

\item ``Economic Sanctions Are Effective Only After the Onset of War.''
\\ \indent \textit{-Central Bank of the Bahamas}, Nassau, Bahamas, January 2023 (Presentation)

\item ``Banking Bad: A Field Experiment on Regulatory Compliance in the Finance Industry.'' 
\\ \indent \textit{-Central Bank of the Bahamas}, Nassau, Bahamas, January 2022 (Presentation)
\\ \indent \textit{-Evidence in Governance and Politics Meeting}, Virtual, October 2021 (Presentation)
\\ \indent \textit{-Central Bank of the Bahamas}, Nassau, Bahamas, January 2021 (Presentation)
\\ \indent \textit{-Central Bank of the Bahamas}, Nassau, Bahamas, January 2020 (Presentation)
\\ \indent \textit{-University of Oxford}, Oxford, UK, Nov 2019 (Presentation)
\\ \indent \textit{-University of Chicago, Harris School}, Chicago, IL, Mar 2018 (Presentation)

\item ``Ex-Combatant Demobilization in Colombia: Evidence from a Resume Experiment.'' (With Oliver Kaplan)
\\ \indent \textit{-Network of European Peace Scientists}, Bologna, Italy, June 2023 (Presentation)
\\ \indent \textit{-Peace Science Society Annual Meeting}, Denver, CO, November 2022 (Presentation)
\\ \indent \textit{-International Studies Association Annual Meeting}, Nashville, TN, March 2022 (Presentation)
\\ \indent \textit{-Evidence in Governance and Politics}, Virtual Meeting, November 2021
\\ \indent \textit{-American Political Science Association Annual Meeting}, Seattle, WA, Sept 2021 (Presentation)
\\ \indent \textit{-International Studies Association Annual Meeting}, Virtual, March 2021 (Presentation)

\item ``The Tyranny of Supply: Natural Resources and Rebel Territorial Control in Civil Conflicts.'' (With Jacob Aronson, Kyosuke Kikuta, and Jim Walsh)
\\ \indent \textit{-American Political Science Association Annual Meeting}, Virtual, August 2020 (Presentation)
\\ \indent \textit{-American Political Science Association Annual Meeting}, Washington DC, August 2018 (Presentation)
\\ \indent \textit{-The College of William and Mary Global Research Institute}, Williamsburg, VA, June 2019 (Presentation)
\\ \indent \textit{-The University of Texas Geography Department}, Austin, TX, April 2018 (Presentation)

%\item ``Territorial Control and Natural Resources During Civil Wars.'' (With Jacob Aronson, Kyosuke Kikuta, and Jim Walsh)
%\\ \indent \textit{-American Political Science Association Annual Meeting}, Washington DC, August 2020 (Presentation)

\item ``Ex-combatant Demobilization and Support for Peace: A Reconciliation Quasi-Experiment in Colombia.'' (With Oliver Kaplan and Joseph K. Young)
\\ \indent \textit{-American Political Science Association Annual Meeting}, Washington DC, August 2019 (Presentation)
\\ \indent \textit{-University of Notre Dame}, South Bend, IN, Feb 2020 (Presentation)


%\item ``Words of Encouragement: A Global Field Experiment on Motivating Development Organizations to Evaluate Impact.'' (With Eliza Riley, James Hodgson, and Daniel Nielson)
%\\ \indent \textit{-American Political Science Association Annual Meeting}, Washington DC, August 2019 (Presentation)

\item ``The Strategic Logic of Targeting of Aid by Rebel Groups During War.'' (With Trey Billing and David Backer)
\\ \indent \textit{-American Political Science Association Annual Meeting}, San Francisco, September 2017 (Presentation)

\item ``Resources of Terror: Natural Resources and Strategies of Conflict.'' (With Andrew Stravers.) 
	\\ \indent \textit{-American Political Science Association Annual Meeting}, Washington DC, August 2018 (Presentation)
	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, IL, April 2016 (Presentation)

\item ``How Government Reactions to Violence Worsen Social Welfare: Evidence from Peru.'' (With Renard Sexton and Rachel Wellhausen.)
	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, IL, April 2016 (Presentation)

\item ``Spoiling Peace Agreements after Civil War: A Synthetic Control Approach Applied to Nicaragua.'' (With Kyosuke Kikuta and Joseph Young)
	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, IL, April 2016 (Presentation)
	\\ \indent \textit{-Workshop on Political Violence, UT Dallas}, Dallas, TX, May 2016

\item ``Aiding Peace: Foreign Aid Donor Behavior in the Democratic Republic of the Congo." (With Susanna Campbell)
	\\ \indent \textit{-International Studies Association Annual Meeting}, Atlanta GA, March 2016 (Presentation)
	\\ \indent \textit{-American Political Science Association Annual Meeting}, San Francisco, September 2015 (Presentation)

%\item ``Electing to Develop: A Field Experiment on Legislators? Endorsements of Aid Promoting Public Goods in 90 Countries'' (With Allen Hicken, Joel Selway, and Daniel Nielson)
%	\\ \indent \textit{-American Political Science Association Annual Meeting}, Washington D.C., September 2014 (Presentation)

\item ``Foreign Aid and Territorial Control in Civil War: A GIS Approach.'' (With Daniel Strandow and Joseph Young)
	\\ \indent \textit{-American Political Science Association Annual Meeting}, San Francisco, September 2015 (Presentation)
	\\ \indent \textit{-International Studies Association Annual Meeting}, Toronto, March 2014 (Presentation)
	
\item ``A Field Experiment on the Liability of Foreignness: 	Country of Origin and U.S. Inward Investment Promotion.'' (With Nate Jensen and Dan Nielson). 
	\\ \indent \textit{International Studies Association Annual Meeting}. San Francisco, CA, April 2013 (Presentation)

%\item ``Reputation Information Asymmetry, and NGO Opportunism: A Randomized Global Field Experiment.'' (With Daniel Nielson, Ryan Bakow, and Brian Reed)
%	\\ \indent \textit{-International Studies Association Annual Meeting}, Toronto, March 2014 (Presentation)
%	\\ \indent \textit{-American Political Science Association Annual Meeting}, Chicago, IL, September 2014 (Presentation)

\item ``Deceptive Studies or Deceptive Answers: Competing Global Field and Survey Experiments on Anonymous Incorporation.'' (With Brock Laney, Daniel Nielson, and J.C. Sharman)
	\\ \indent \textit{Columbia University, Center for the Study of Development Strategies}, New York, November 	2013 (Presentation)
	\\ \indent \textit{University of California, San Diego, Laboratory on International Law and Regulation}, November 2013 San Diego, (Presentation)

\item ``The Local Geography of Transnational Terrorist Attacks.'' (With Alex Braithwaite, Josiah Marineau, and Joseph K. Young)
	\\ \indent \textit{-International Studies Association Annual Meeting}, New Orleans, March 2015 (Presentation)
	\\ \indent \textit{-International Studies Association Annual Meeting}, Toronto, March 2014 (Presentation)
	\\ \indent \textit{-Uppsala Workshop on Geography and Armed Conflict}, Uppsala, October 2013 (Presentation)
	\\ \indent \textit{-Texas A\&M Department of Political Science}, College Station, October 2013.	(Presentation)

\item ``Obligated to Deceive? Aliases, Confederates, and the Common Rule in International Field Experiments.'' (With Daniel L. Nielson).
	\\ \indent \textit{-University of California, San Diego, Ethics in Comparative Politics Experiments Workshop}, San Diego, May 2013 (Presentation)
	\\ \indent \textit{-American Political Science Association, Roundtable on Ethics in Comparative Politics Experiments}, Washington D.C., September 2013 (Roundtable) 

%\item ``Status on the Street: A Field Experiment of how Socio-economic Status Affects Prosocial Behavior.'' (With Matt Brigham, Peter Carroll, Madeleine Gleave, Brock Laney, Catherine Nielson, and Daniel Nielson.)
%	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, April 2013 (Presentation)

%\item ``Aversion to Learning in Development? A Global Field Experiment on Microfinance Institutions MFI Experiment.'' (With Matthew Brigham, William Matthias, Chase Petrey, and Daniel Nielson).
%	\\ \indent \textit{-International Studies Association Annual Meeting}, San Francisco, April 2013 (Presentation)

\item ``Elite and Mass Support for Foreign Aid in Recipient Countries: A Field Experiment in Uganda.'' (With Helen Milner, Adam Harris, and Dan Nielson).
	\\ \indent \textit{-University of Pittsburgh}, Pittsburgh, PA, April 2015 (Presentation)
	\\ \indent \textit{-Princeton Foreign Aid Workshop}, Princeton, NJ, April 2013 (Presentation)
	\\ \indent \textit{-American Political Science Association Meeting}, Chicago, August 2013 (Presentation)
	\\ \indent \textit{-Midwest Political Science Association Meeting}, Chicago, April 2013 (Presentation)
	
\item ``Foreign Aid and Government/Rebel Control Zones in Civil War: A GIS Approach.'' (With Daniel Strandow).
	\\ \indent \textit{-Climate Change and African Political Stability (CCAPS) ``Shifting Conflict Patterns in Africa'' Conference}, Austin, April 2013 (Presentation)

\item ``Extrinsic, Intrinsic, and Social Incentives for Crowdsourcing Development Information in Uganda: A Field Experiment.'' (With Robert Morello*, Maddy Gleave, and Daniel Nielson). 
	\\ \indent \textit{-United Nations Development Program M\&E for ICT}, Nairobi, Kenya, October 2013 (Presentation)	
	\\ \indent \textit{-International Studies Association Annual Meeting}, San Francisco, CA, April 2013  (Presentation)
	\\ \indent \textit{-African Studies Academy, University of North Carolina, Charlotte}, Charlotte, NC, February 2013 (Presentation)
	
\item Co-organizer of two conferences on ``Field Experiments in International Relations.'' (With Daniel Nielson and Helen Milner). 
	\\ \indent -Princeton, NJ, Spring 2014  
	\\ \indent -Park City, UT, Sept 2012
	
\item ``Endorsements of Foreign Aid Types: A Global Field Experiment of Members of Parliament.'' (With Daniel Nielson and Joel Selway)
	\\ \indent \textit{-Field Experiments in International Relations}, Park City, UT, September 2012 (Presentation)

\item ``Using Field Experiments in International Relations: A Randomized Study of Anonymous Incorporation.'' (With Daniel Nielson and J.C. Sharman). 
	\\ \indent \textit{-Field Experiments in International Relations}, Park City, UT, September 2012 (Presentation)

\item ``Which Devil in Development? A Large-N Survey and Randomized Field Experiment Comparing Bilateral Aid, Multilateral Assistance, and Government Action in Uganda.'' (With Helen Milner and Daniel Nielson)
	\\ \indent \textit{-Best Practices in Experiments Conference}, Princeton University, Princeton, NJ, September 2012 (Presentation)
	\\ \indent \textit{-American Political Science Association Annual Meeting}, New Orleans, September 2012 (Presentation)

\item ``Orchestrating the Fight Against Anonymous Incorporation: A Field Experiment.'' (With Daniel Nielson and J.C. Sharman)
	\\ \indent \textit{-Orchestration in International Relations Workshop}, Munich, Germany, May 2012

\item ``Modeling Dynamic Violence: Integrating Events Data Analysis and Agent-Based Modeling.'' (With Stephen Shellman and Joseph K. Young)
	\\ \indent \textit{-International Studies Association Annual Meeting}, San Diego, March 2012 (Presentation)
	\\ \indent \textit{-International Studies Association Annual Meeting}, Montreal, Canada, March 2011 (Presentation)
	\\ \indent \textit{-American Political Science Association}, Washington D.C., September 2010 (Presentation)

\item ``The Downstream Effects of Combatant Fragmentation in Civil Wars.'' (With Peter Rudloff)
	\\ \indent \textit{-International Studies Association Annual Meeting}, Montreal, Canada, March 2011 (Presentation)

\item ``The Causes of Non-Compliance with International Law: Evidence from a Field Experiment on Financial Transparency.'' (With Daniel Nielson and J.C. Sharman). 
	\\ \indent \textit{-Texas Triangle Conference}, College Station, TX, March 2013.
	\\ \indent \textit{-Oklahoma State University Department of Political Science}, Stillwater, OK, March 2013 (Presentation)
	\\ \indent \textit{-University of Illinois Department of Political Science}, Champaign, IL, October 2012 (Presentation)
	\\ \indent \textit{-American Political Science Association Annual Meeting}, New Orleans, September 2012 (Presentation)
	\\ \indent \textit{-Tools of International Pressure: How International Actors Influence Domestic Politics in Sovereign States}, Yale University, May 2012 (Presentation)
	\\ \indent \textit{-Evidence in Governance and Politics Network}, Vancouver, Canada, April 2012 (Presentation)
	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, April 2012 (Presentation)
	\\ \indent \textit{-International Studies Association Annual Meeting}, San Diego, March-April 2012 (Presentation)
	\\ \indent \textit{-Department of Statistics, Brigham Young University}, Provo, January 2012 (Presentation)
	
\item ``Terrorism, Spoiling, and the Resolution of Civil Wars.'' (With Joseph K. Young).
	\\ \indent \textit{-American Political Science Association Annual Meeting}, Chicago, August 2013 (Presentation)
	\\ \indent \textit{-Midwest Political Science Association}, Chicago, April 2013.	
	\\ \indent \textit{-International Studies Association}, New Orleans, February 2010 (Presentation)
	\\ \indent \textit{-International Studies Association}, New York, February 2009 (Presentation)
	\\ \indent \textit{-Peace Science Society International}, Claremont, October 2008 (Presentation)
	\\ \indent \textit{-Midwest Political Science Association}, Chicago, April 2008 (Presentation)


\item ``Bargaining and the Interdependent Stages of Civil War Resolution.'' \textit{Journal of Conflict Resolution.}
%	\\ \indent -Rank-- ISI:  9 of 141 (I. Factor: 1.883); Garand/Giles 2009: 10 of 92.
	\\ \indent \textit{-Oklahoma State University, Political Science (Invited)}, June 2008 (Presentation)
	\\ \indent  \textit{-New Faces in Security Studies (Invited)}, Triangle Institute for Security Studies, Duke University, September 2006 (Presentation)
	\\ \indent \textit{-Program in Arms Control, Disarmament, and International Security Colloquium Series: Conflict and Security (Invited)}, UIUC, April 2006 (Presentation)

\item ``Terrorism and Civil War: A Spatial and Temporal Approach to a Conceptual Problem.'' (With Joseph K. Young). \textit{Perspectives on Politics}. 
%	   \\ \indent -Rank-- ISI: 20 of 141 (I. Factor: 1.519); Garand/Giles 2009: 11 of 92.
	   \\ \indent \textit{-International Studies Association Annual Meeting}, Montreal, Canada, March 2011 (Presentation)
	   \\ \indent \textit{-American Political Science Association}, Washington D.C., September 2010 (Presentation)


\item ``Is Ethnicity Identifiable? Lessons from an Experiment in South Africa.'' (With Adam Harris). \textit{Journal of Conflict Resolution}.
%	\\ \indent -Rank-- ISI:  9 of 141 (I. Factor: 1.883); Garand/Giles 2009: 10 of 92.
    	\\ \indent \textit{-Midwest Political Science Association}, Chicago, April 2009 (Poster)
    	\\ \indent \textit{-University of Fort Hare}, East London, South Africa, November 2008 (Presentation)

\item ``Combatant Fragmentation and the Dynamics of Civil Wars.'' (With Peter Rudloff). \textit{British Journal of Political Science}. 
%	\\ \indent -Rank-- ISI:  11 of 141 (I. Factor: 1.822); Garand/Giles: 4 of 92.
    	\\ \indent \textit{-American Political Science Association}, Toronto, Sept 2009 (Presentation)
    	\\ \indent \textit{-Midwest Political Science Association}, Chicago, April 2009 (Presentation)
    	\\ \indent \textit{-International Studies Association}, San Francisco, March 2008 (Presentation)

\item ``More Combatant Groups, More Terror? Empirical Tests of an Outbidding Logic.'' (With Joseph K. Young). \textit{Terrorism and Political Violence}. 
%	\\ \indent -Rank-- ISI:  59 of 141 (I. Factor: 0.814); Garand/Giles: Not considered.
	\\ \indent \textit{-International Studies Association}, New Orleans, February 2010 (Presentation)

\item ``Can Peace Be Purchased? A Sectoral-Level Analysis of Aid's Influence on Transnational Terrorism'' (With Joseph K. Young). \textit{Public Choice}.
%	\\ \indent -Rank-- ISI:  48 of 141 (I. Factor: 0.894); Garand/Giles: 35 of 92; Combes \& Linnemer: 59 of 600.
	 \\ \indent \textit{-American Political Science Association Annual Meeting}, Seattle, WA, Sept 2011 (Presentation)
	 \\ \indent \textit{-Terrorism and Policy Conference}, University of Texas, Dallas, May 2011 (Invited)
	 \\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, Illinois, April 2011 (Presentation)

\item ``The Localized Geography of Foreign Aid: A New Dataset and Application to Violent Armed Conflict.'' (With Josh Powell, Daniel Strandow, and Jeff Tanner). \textit{World Development}.
%	\\ \indent -Rank-- ISI:  57 of 305 (I. Factor: 1.612); Garand/Giles: Not considered; Combes \& Linnemer: 34 of 600.
	\\ \indent \textit{-Uppsala Department of Peace and Conflict Forum}, Uppsala, Sweden, May 2010 (Presentation)
	\\ \indent \textit{-World Bank Conflict and Fragility Innovation Fair (Invited)}, Cape Town, SA, April 2010 %    (Presentation)
	\\ \indent \textit{-AidData: Aid Transparency and Development Finance}, Oxford, UK, March 2010 (Presentation)
	
\item ``More Dollars Than Sense: Refining Our Knowledge of Development Finance Using AidData.'' (With Michael Tierney, Daniel L. Nielson, Darren G. Hawkins, J. Timmons Roberts, Ryan M. Powers, Bradley Parks, Sven E. Wilson, Robert L. Hicks.) \textit{World Development}. 
%	\\ \indent -Rank-- ISI:  57 of 305 (I. Factor: 1.612); Garand/Giles: Not considered; Combes \& Linnemer: 34 of 600.
	\\ \indent \textit{-AidData: Aid Transparency and Development Finance}, Oxford, UK, March 2010 (Presentation)
	\\ \indent \textit{-PLAID Data Vetting Workshop}, Henry Stimson Center, Washington D.C., September 2009 (Presentation)

\item ``Promise and Pitfalls of Terrorism Research.'' (With Joseph K. Young). \textit{International Studies Review}. 
%	\\ \indent -Rank-- ISI: 61 of 141 (I. Factor: 0.803). Garand/Giles: Not considered.
   	\\ \indent \textit{-Midwest Political Science Association}, Chicago, April 2009 (Presentation)                                  

\item ``Foreign Aid Shocks as a Cause of Violent Armed Conflict.'' (With Richard A. Nielsen, Zachary S. Davis, Tara Candland, and Daniel L. Nielson). \textit{American Journal of Political Science}.  
%	\\ \indent -Rank-- ISI:  3 of 141 (I. Factor: 2.588); Garand/Giles: 2 of 92.
   	\\ \indent \textit{-Uppsala Forum for Peace, Democracy, and Justice}, Uppsala, Sweden, May 2010 (Presentation)
   	\\ \indent \textit{-International Studies Association}, San Francisco, March 2008 (Presentation)

\item ``Just Part of the Game?: Arms Races, Rivalry, and Competition.'' (With Toby J. Rider and Paul F. Diehl). \textit{Journal of Peace Research}. 
%	\\ \indent -Rank-- ISI:  22 of 141 (I. Factor: 1.476); Garand/Giles: 38 of 92.
    	\\ \indent \textit{-Midwest Political Science Association}, Chicago, April 2008 (Presentation)

\item ``Rumor Dynamics in Ethnic Violence.'' (With Ravi Bhavnani and James Kuklinski). \textit{Journal of Politics}. 
%	\\ \indent -Rank-- ISI:  24 of 141 (I. Factor: 1.426); Garand/Giles: 3 of 92.
	\\ \indent \textit{-American Political Science Association Annual Meeting}, Washington, D.C., September 2005 (Presentation)
	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, April 2005 (Presentation)
	\\ \indent \textit{-Merriam Lab Junior Master Class (Invited)}, Urbana, IL, October 2004 (Presentation)

\item ``Agents and Conflict: Adaptation and the Complexity of War.'' \textit{Complexity}. 
%	\\ \indent -Rank-- ISI:  24 of 93 (I. Factor: 1.367); Garand/Giles: Not considered (Mathematics Journal).
	\\ \indent \textit{-Complex Systems Symposium}, Physics Department, UIUC, May 2006 (Invited Plenary Talk)

\item ``Fighting Fire with Fire?: How (Not) to Neutralize an Insurgency.'' (With Joseph K. Young). \textit{Civil Wars}. 
%	\\ \indent -Not Ranked in ISI or Garand/Giles.
	\\ \indent \textit{-International Studies Association Annual Meeting}, San Diego, March 2006 (Presentation)

\item ``Accounting for the Unaccounted: Weak-Actor Social Structure in Asymmetric Wars.'' (With Scott Edwards). \textit{International Studies Quarterly}. 
%	\\ \indent -Rank-- ISI:  19 of 141 (I. Factor: 1.523); Garand/Giles: 9 of 92.
	\\ \indent \textit{-International Studies Association Annual Meeting}, Honolulu, March 2005 (Presentation)
	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, April 2004 (Presentation)

\item ``Rethinking Third Party Interventions into Civil Wars: An Actor-Centric Approach.'' (With Tze Kwang Teo). \textit{Journal of Politics}. 
%	\\ \indent -Rank-- ISI:  24 of 141 (I. Factor: 1.426); Garand/Giles: 3 of 92.
	\\ \indent \textit{-Political Methodology Summer Meeting}, Tallahassee, July 2005 (Poster)
	\\ \indent \textit{-Midwest Political Science Association Annual Meeting}, Chicago, April 2005 (Presentation)
\end{itemize}


%\subsection*{Research Areas}
%\begin{itemize} \setlength{\itemsep}{1pt}
%\item Political Violence 
%\item International Development Aid
%\item Experiments 
%\end{itemize}



\section*{FELLOWSHIPS, GRANTS, AND AWARDS}

\subsection*{External Grants \& Honors}

\begin{itemize}\setlength{\itemsep}{1pt}

\item Nigeria Independence Award, \textit{Nigerian Government via U.S. Nigerian Embassy}, 2025--2026.

\item Fellowship at the Institute for Advanced Study in Toulouse (IAST), \textit{Toulouse School of Economics}, 2024--2025.

\item \textit{Russell Sage Foundation, Policing Socio-geographic Change and Displacement, \$187,136} (With Hannah Walker, Derek Epp, and Amy Liu). 

\item \textit{Lijphart/Przeworski/Verba award for the best data set in comparative politics, Honourable Mention (second place), 2023.}

\item \textit{Jameel Poverty Action Lab, Crime and Violence Initiative, \$41,682.30, 2022--2023, with LSE and Washington University, St. Louis}

\item \textit{World Bank, Stolen Assets Recovery Initiative (StAR), \$40,000, 2021--2022}

\item \textit{Cambridge University, \$25,000, 2020--2021}

\item \textit{United States Agency for International Development, Democracy, Rights, and Governance, multi-million dollar ongoing consortium contract, 2018--2023}.

\item \textit{United States Institute of Peace, Chinese Engagement in the South Sudanese Peace Process, \$45,000, 2018--2019}

\item \textit{National Science Foundation, Interdisciplinary Behavioral and Social Sciences Research (IBSS), \$250,000 consortium grant}, (With Michigan, Maryland, BYU)

\item \textit{Honorable Mention for the Best Book Award by the International Law (ILAW) section of the International Studies Association}, 2015

\item \textit{Yale H. Ferguson Award for the book that most advances the vibrancy of international studies as a pluralist discipline by the International Studies Association, Northeast}, 2015

\item \textit{University of Illinois, Urbana-Champaign Department of Political Science Alumnus of the Year}, 2015. 

\item \textit{2014 Prize for Best Article by the National Consortium for the Study of Terrorism and Responses to Terrorism (START)}, For ``Terrorism and Civil War: A Spatial and Temporal Approach to a Conceptual Problem.'' (With Joseph K. Young).

\item \textit{Swiss Network for International Studies (SNIS), \$256,000 consortium grant}, (With the Graduate Institute of Geneva), 2014--2016.

\item \textit{2013 Prize for Best Paper in the Experimental Section presented at the previous year's APSA}, For ``Causes of Non-Compliance with International Law: Evidence from a Field Experiment on Financial Transparency.'' (With Daniel Nielson and J.C. Sharman).

\item \textit{2013 McGillivray Prize for Best Paper in Political Economy presented at the previous year's APSA}, For ``Causes of Non-Compliance with International Law: Evidence from a Field Experiment on Financial Transparency.'' (With Daniel Nielson and J.C. Sharman).

\item \textit{Department of Defense Minerva Program, \$800,000 consortium grant}, (With UNCC, Penn State, SUNY-Albany), 2013--2016.

\item \textit{USAID Higher Education Solutions Network Grant to AidData for Geocoding Foreign Aid, \$25 million consortium grant}, (With William and Mary, Brigham Young University, Development Gateway, and ESRI) 2012-2017.

\item \textit{AidData: Tracking Development Finance, \$1 million, Hewlett Foundation}, (With Michael Tierney, Daniel Nielson, Robert Hicks, Timmons Roberts, Darren Hawkins, and Sven Wilson.) 2010-2013. 

\item \textit{AidData: Tracking Development Finance, \$1.5 million, Gates and Hewlett Foundations}, (With Michael Tierney, Daniel Nielson, Robert Hicks, Timmons Roberts, Darren Hawkins, and Sven Wilson.) 2008--2009.

\item \textit{African Development Bank Mapping Initiative, Phase 1, \$75,000}, (With Michael Tierney, Robert Hicks, Timmons Roberts, Darren Hawkins, and Sven Wilson.) Spring 2011

\item \textit{World Bank Mapping for Results Initiative, Phase 2, \$150,000}, Washington D.C., Spring 2011

\item \textit{World Bank Mapping for Results Program on Georeferencing Foreign Aid Data, Phase 1}, Washington D.C., 2010

\item \textit{National Science Foundation Grant} ``Terror, Conflict Processes, Organizations, \& Ideologies: Completing the Picture.'' Award \# BCS-0904883, \$467,000. (With Shellman, Stephen, Ryan Bakker, Remco Chang, and Joseph Young.) 2009--2012.

\item \emph{Peace Scholar Dissertation Fellow}, United States Institute of Peace, AY 2006--2007

\item \emph{Selected for Participation in the 7th Annual ``New Faces in Security Studies'' Conference},
Triangle Institute for Security Studies, Duke University, September 2006

\item \emph{Howard Penniman Graduate Scholarship}, Pi Sigma Alpha National Office, 2002--2003.

\end{itemize}





\subsection*{Internal Grants \& Honors}

\begin{itemize}\setlength{\itemsep}{1pt}

\item \emph{Frank C. Erwin, Jr. Centennial Professor of Government, College of Liberal Arts}, University of Texas at Austin, 2021--present.

\item Nominated for the \emph{UT Experiential Learning Excellence Award}, University of Texas at Austin, 2023.

\item \emph{Fellow of the Bannister Chair, College of Liberal Arts}, University of Texas at Austin, 2012--2021.

\item \emph{Fellow of the Wilson Chair, College of Liberal Arts}, University of Texas at Austin, 2015--2020.

\item \emph{Internal Research Grants at BYU, Totaling \$110,000}, Brigham Young University, 2007--2012.

\item \textit{Pi Sigma Alpha Outstanding Faculty Award} Brigham Young University, April 2010

\item Kathleen Burkholder Award for the best dissertation defended/deposited in 2007/2008, UIUC Department of Political Science

\item Dissertation nominated by the UIUC Political Science Department for APSA and Peace Science best dissertation awards

\item \emph{Scott Dissertation Completion Fellowship}, Graduate College, UIUC, AY
2006--2007 (awarded, but I declined)

\item \emph{Rita and Leonard Ogren Award for Academic Achievement}, Department of Political
Science, UIUC, February 2006.

\item \emph{ACDIS Thesis Initiation Fellowship}, Program in Arms Control, Disarmament, and International
Security, UIUC, AY 2005--2006.

\item \emph{Foreign Language and Area Studies Fellowships}, The Russian, East European, and Eurasian
Center, UIUC, AY 2004--2005 \& 2003--2004.

\item \emph{Charles Merriam Fellowship}, Department of Political Science, UIUC, 2002--2005.

\end{itemize}



\section*{TEACHING}
\subsection*{Recognition}
\begin{itemize}\setlength{\itemsep}{1pt}

\item Provost's Teaching Fellow, University of Texas at Austin, 2020--2022

\item Nominated for the Provost's Distinguished Service Academy, 2020

\item Nominated by UT Government Department for the university Joe and Bettie Branson Ward Excellence Award, 2018--2019.

\item Nominated by UT College of Liberal Arts and UT Government Department for the university William David Blunk Memorial Professorship, 2017--2018.

\item Nominated by UT College of Liberal Arts and UT Government Department for the university Joe and Bettie Branson Ward Excellence Award, 2015--2016

\item Liberal Arts Student Council Endowed Teaching Award, UT Austin, 2013--2014

\item Pi Sigma Alpha Political Science Honor Society, BYU Chapter, Outstanding Professor 2009--2010

\item Advanced Graduate Teacher Certificate, UIUC, April 2006.

\item Graduate Teacher Certificate, UIUC, May 2004.

\item ``List of Teachers Ranked Excellent By Their Students'' \\ \indent \textit{- Intro. to International Relations},
UIUC, Fall 2005.  \\ \indent \textit{- Intro. to Comparative Politics}, UIUC, Summer 2004.
\end{itemize}



\subsection*{Faculty Experience (And Overall Ratings)}
\begin{itemize}\setlength{\itemsep}{1pt}

\item \textit{Public Policy Evaluation (graduate)}
\\ \indent Fall 2025, UT Austin (Overall Course: 4.22/5.0; Overall Instructor: 4.56/5.0)
\\ \indent Spring 2018, UT Austin (Overall Course: 4.1/5.0; Overall Instructor: 4.3/5.0)

\item \textit{International Development \& Global Justice (undergraduate)}
\\ \indent Spring 2025, UT Austin (Overall Course: 4.15/5.0; Overall Instructor: 4.37/5.0)

\item \textit{Terrorism (undergraduate)}
\\ \indent Spring 2025, UT Austin (Overall Course: 4.52/5.0; Overall Instructor: 4.59/5.0)
\\ \indent Spring 2022, UT Austin (Overall Course: 4.2/5.0; Overall Instructor: 4.4/5.0)
\\ \indent Fall 2020, UT Austin (Overall Course: 4.5/5.0; Overall Instructor: 4.6/5.0) [Asynchronous hybrid; COVID]
\\ \indent Spring 2019, UT Austin (Overall Course: 3.8/5.0; Overall Instructor: 4.2/5.0)
\\ \indent Spring 2017, UT Austin (Overall Course: 4.2/5.0; Overall Instructor: 4.5/5.0)
\\ \indent Spring 2013, UT Austin (Overall Course: 4.2/5.0; Overall Instructor: 4.5/5.0)
\\ \indent Fall 2011, BYU  (Overall Course: 7.2/8.0; Overall Instructor: 7.5/8.0) 
\\ \indent Winter 2009, BYU (Overall Course: 7.3/8.0; Overall Instructor: 7.6/8.0)
\\ \indent Fall 2008, BYU (Overall Course: 7.3/8.0; Overall Instructor: 7.3/8.0) 


\item \textit{Introduction to Economic Institutions, History, and Principles (ECON 1500; undergraduate)}
\\ \indent Fall 2024, Utah State University (Overall Course: 4.2/5.0; Overall Instructor: 4.4/5.0)

\item \textit{Peacebuilding \& Development (POLS 4990; undergraduate)}
\\ \indent Fall 2024, Utah State University (Overall Course: 4.0/5.0; Overall Instructor: 4.4/5.0)


\item \textit{Scope and Methods (graduate)}
\\ \indent Fall 2024, UT Austin (Overall Course: 3.82/5.0; Overall Instructor: 4.18/5.0)
\\ \indent Fall 2023, UT Austin (Overall Course: 4.33/5.0; Overall Instructor: 4.83/5.0)
\\ \indent Fall 2022, UT Austin (Overall Course: 3.8/5.0; Overall Instructor: 4.4/5.0)
\\ \indent Fall 2021, UT Austin (Overall Course: 4.2/5.0; Overall Instructor: 4.8/5.0) [Synchronous online; COVID]
\\ \indent Fall 2020, UT Austin (Overall Course: 4.1/5.0; Overall Instructor: 5.0/5.0) [Synchronous online; COVID]
\\ \indent Fall 2018, UT Austin (Overall Course: 3.1/5.0; Overall Instructor: 4.3/5.0)
\\ \indent Fall 2016, UT Austin (Overall Course: 3.4/5.0; Overall Instructor: 4.3/5.0)
\\ \indent Fall 2015, UT Austin (Overall Course: 4.1/5.0; Overall Instructor: 4.7/5.0)
\\ \indent Fall 2014, UT Austin (Overall Course: 4.4/5.0; Overall Instructor: 4.9/5.0)

\item \textit{Political Violence (graduate)}
\\ \indent Spring 2024, UT Austin (Overall Course: 4.67/5.0; Overall Instructor: 5.0/5.0)
\\ \indent Spring 2022, UT Austin (Overall Course: 4.2/5.0; Overall Instructor: 4.7/5.0)
\\ \indent Spring 2020, UT Austin (Overall Course: 4.8/5.0; Overall Instructor: 4.8/5.0) [Synchronous online; COVID]
\\ \indent Spring 2018, UT Austin (Overall Course: 4.1/5.0; Overall Instructor: 4.3/5.0)
\\ \indent Spring 2015, UT Austin (Overall Course: 4.7/5.0; Overall Instructor: 4.7/5.0)
\\ \indent Spring 2013, UT Austin (Overall Course: 4.6/5.0; Overall Instructor: 4.6/5.0)

\item \textit{Civil Wars and Ethnic Violence (undergraduate)}
\\ \indent Spring 2024, UT Austin (Overall Course: 4.15/5.0; Overall Instructor: 4.25/5.0)
\\ \indent Spring 2021, UT Austin (Overall Course: 2.9/5.0; Overall Instructor: 3.1/5.0), [Asynchronous hybrid; COVID]
\\ \indent Fall 2019, UT Austin (Overall Course: 3.9/5.0; Overall Instructor: 4.3/5.0)
\\ \indent Fall 2017, UT Austin (Overall Course: 4.2/5.0; Overall Instructor: 4.2/5.0)
\\ \indent Fall 2013, UT Austin (Overall Course: 3.9/5.0; Overall Instructor: 4.2/5.0)
\\ \indent Fall 2012, UT Austin (Overall Course: 4.5/5.0; Overall Instructor: 4.5/5.0)
\\ \indent Fall 2011, BYU (Overall Course: 7.5/8.0; Overall Instructor: 7.6/8.0)
\\ \indent Fall 2009, BYU (Overall Course: 7.6/8.0; Overall Instructor: 7.2/8.0)
\\ \indent Winter 2008, BYU (Overall Course: 6.8/8.0; Overall Instructor: 7.0/8.0)
\\ \indent Fall 2007, BYU (Overall Course: 7.1/8.0; Overall Instructor: 7.3/8.0) 

\item \textit{IPD Research Practicum (undergraduate)}
\\ \indent Spring 2023, UT Austin (Overall Course: 4.8/5.0; Overall Instructor: 4.8/5.0) 
\\ \indent Fall 2022, UT Austin (Overall Course: 3.6/5.0; Overall Instructor: 4.0/5.0) 

\item \textit{Data Science (undergraduate; asynchronous online)}
\\ \indent Summer 2021, UT Austin (Overall Course: 3.3/5.0; Overall Instructor: 3.9/5.0) [Asynchronous online; COVID]
\\ \indent Summer 2020, UT Austin (Overall Course: 4.3/5.0; Overall Instructor: 4.6/5.0) [Asynchronous online; COVID]

\item \textit{Experimental Methods in Political Science (graduate)}
\\ \indent Spring 2021, UT Austin (Overall Course: 4.0/5.0; Overall Instructor: 4.3/5.0), [Synchronous online; COVID]
\\ \indent Spring 2019, UT Austin (Overall Course: 3.0/5.0; Overall Instructor: 3.5/5.0) 
\\ \indent Fall 2016, UT Austin (Overall Course: 4.9/5.0; Overall Instructor: 4.9/5.0)
\\ \indent Fall 2013, UT Austin (Overall Course: 3.1/5.0; Overall Instructor: 3.9/5.0)

\item \textit{Seminar on Intensive Fieldwork Training (SIFT) (graduate)}
\\ \indent Spring 2020, UT Austin (Overall Course: 3.8/5.0; Overall Instructor: 4.8/5.0), [Synchronous online; COVID]

\item \textit{Research in International Politics}
\\ \indent Spring 2016, UT Austin (Overall Course: 4.8/5.0; Overall Instructor: 5.0/5.0)

\item \textit{Experimental Methods for Impact Evaluation (graduate; LBJ School}
\\ \indent Spring 2017 (Overall Course: 4.4/5.0; Overall Instructor: 4.5/5.0)
\\ \indent Spring 2016 (Overall Course: 4.3/5.0; Overall Instructor: 4.7/5.0)

\item \textit{Violence in the Age of Peace (undergraduate signature course)}
\\ \indent Fall 2015, UT Austin (Overall Course: 3.5/5.0; Overall Instructor: 4.1/5.0)


\item \textit{Field Experiments (graduate; LBJ School}
\\ \indent Spring 2013 (Overall Course: 3.3/5.0; Overall Instructor: 4.0/5.0)

\item \textit{Field Experiments in Peacebuilding (undergrdaute)}
\\ \indent Fall 2010 (Overall Course: 7.1/8.0; Overall Instructor: 7.3/8.0)
\\ \indent Fall 2009 (Overall Course: 7.4/8.0; Overall Instructor: 7.7/8.0) 

\item \textit{Quantitative Political Methodology (undergraduate)}
%\\ \indent Winter 2012, BYU (Overall Course: In Progress; Overall Instructor: In Progress) 
\\ \indent Fall 2010, BYU (Overall Course: 6.1/8.0; Overall Instructor: 7.0/8.0)
\\ \indent Winter 2010, BYU (Overall Course: 6.0/8.0; Overall Instructor: 7.2/8.0) 

\item \textit{Intro to International Relations (undergraduate)}
\\ \indent Winter 2009, BYU  (Overall Course: 6.7/8.0; Overall Instructor: 7.1/8.0) 

\item \textit{Capstone Seminar: Political Violence (undergraduate)}
\\ \indent Fall 2008, BYU (Overall Course: 7.3/8.0; Overall Instructor: 7.6/8.0)
\\ \indent Winter 2008, BYU (Overall Course: 6.8/8.0; Overall Instructor: 7.2/8.0)

\end{itemize}







\section*{PROFESSIONAL ACTIVITIES}

\subsection*{Professional Memberships}

\begin{itemize}\setlength{\itemsep}{1pt}
\item American Political Science Association
\item Evidence in Governance \& Politics
\item Peace Science Society
\item International Studies Association
\item Midwest Political Science Association
\end{itemize}

\subsection*{Service}

\subsubsection*{Discipline}

\begin{itemize}\setlength{\itemsep}{1pt}
\item \textit{J. David Singer Data Innovation Award Committee}, APSA Conflict Processes Section, 2025.
\item \textit{Editorial Board}, American Journal of Political Science, 2021--2023.
\item \textit{Discussant for Impact Evidence panel}, Latin American Studies Association, May 2021.
\item \textit{Discussant for The Economics of Violence panel}, American Political Science Association, August 2019.
\item \textit{Discussant for Rebel Institutions and Interests panel}, American Political Science Association, August 2019.
\item \textit{Editorial Board}, International Interactions, 2019--2024.
\item \textit{Discussant for Non-state actors in Armed Conflict panel}, Southern Political Science Association, January 2019.
\item \textit{Peace Science Society International Conference Host} Austin, November 2018
\item \textit{Discussant for The Development Dance: How Donors and Recipients Negotiate Foreign Aid} Book by Haley Swedlund, International Studies Association, April 2018.
\item \textit{Discussant for Resisting War: How Communities Protect Themselves Book by Oliver Kaplan}, International Studies Association, April 2018.
\item \textit{World Bank Open Government Practice Steering Committee}, 2017--present.
\item \textit{Peace Science Society (International), Councilor}, 2017--2021.
\item \textit{American Journal of Political Science New Editor Search Committee}, Midwest Political Science Association, 2016--2017
\item \textit{SPSA Experiments Section Chair for 2017 Program}, 2017 Meeting.
\item \textit{APSA Experiments Section Chair for 2016 Program}, 2016 Meeting.
\item \textit{Editorial Board, \textit{Political Research Quarterly}, Western Political Science Association, 2016--2018}.
\item \textit{Evidence in Governance and Politics Network Membership Round Chair}, Spring 2016.
\item \textit{Evidence in Governance and Politics Network Developing Country Recruitment Round Chair}, Summer 2014.
\item \textit{APSA Experiments Section Chair of Best Paper Award Committee}, 2014 Meeting.
\item \textit{Discussant for ``Crowdsourcing in the Study of Violence'' Panel}, International Studies Association, March 2013.
\item \textit{Chair and Organizer of ``New Directions in Experiments in International Relations'' Panel}, International Studies Association, March 2013. 
\item \textit{Editorial Board, \textit{Foreign Policy Analysis}, International Studies Association Journal, 2013--2015}.
\item \textit{Registry for International Development Impact Evaluations (RIDIE) Task Force}, 3ie and RAND Corporation, 2012--2013.
\item \textit{Discussant for ``Political Violence, Conflict, and Mobilization'' Panel}, Midwest Political Science Association, April 2013.
\item \textit{Discussant for ``State Characteristics and Civil Wars'' Panel}, Midwest Political Science Association, April 2008.
\item \textit{Manuscript Review:} \textit{American Political Science Review}; \textit{American Journal of Political Science}; \textit{Journal of Politics}; \textit{International Studies Quarterly}; \textit{Journal of Conflict Resolution}; \textit{Journal of Peace Research}; \textit{International Organization}; \textit{Perspectives on Politics}; \textit{Foreign Policy Analysis}; \textit{Comparative Political Studies}; \textit{International Studies Review}; \textit{International Interactions}; \textit{Conflict Management and Peace Science}; \textit{Civil Wars}; \textit{Review of International Organizations}; \textit{Review of International Political Economy}; \textit{Grawemeyer World Order Award}; \textit{National Science Foundation}; \textit{Social Science Journal}; \textit{Public Choice}; \textit{Terrorism and Political Violence}; \textit{British Journal of Political Science}; \textit{Security Studies}; \textit{Journal of Experimental Political Science}; \textit{Oxford Economic Papers (OEP)}; \textit{Political Science Research and Methods}; \textit{Journal of Global Security Studies}; \textit{Public Finance Review}; \textit{Political Research Quarterly}; \textit{Research and Politics}; \textit{Journal of Management Studies}; \textit{Czech Journal of International Relations}; \textit{Journal of Global Ethics}; \textit{National Science Foundation}; \textit{Patient-Centered Outcomes Research Institute}; \textit{American Economic Journal: Applied Economics}; \textit{European Journal on Criminal Policy and Research}; \textit{PLOS One}; \textit{Israel Science Foundation}; \textit{International Journal of Qualitative Methods}; \textit{William and Mary TRIP}.
\end{itemize}

\subsubsection*{College and University}

\begin{itemize}\setlength{\itemsep}{1pt}
\item Texas Orange Jackets (UT's oldest historically female service and spirit organization) Roundtable, March 2024.
\item College of Liberal Arts Committee on Endowed Chairs and Professorships, 2021.
\item Experiential Learning Ambassador, University Program, Jan 2018--Dec 2020
\item College of Liberal Arts Committee on Psychology Department lab space, Fall 2017--Spring 2019
\item \textit{UT Austin College of Liberal Arts Randy Diehl Prize in Liberal Arts Scholarship Committee}, 2016--2018
\item \textit{Chair, University Committee on Financial Aid for Students}, UT-Austin, AY 2015--2016.
\item \textit{University Committee on Financial Aid for Students}, UT-Austin, AYs 2013--2016.
\item \textit{Bridging Disciplines Faculty Panel for Conflict Resolution and Peace Studies}, UT-Austin, 2015--present.


\end{itemize}

\subsubsection*{Department}

\begin{itemize}\setlength{\itemsep}{1pt}
\item \textit{Department of Government Executive Committee}, 2025--2026.
\item \textit{Government Department Graduate Annual Review Committee}, AY 2024--2025. 
\item \textit{Department of Government Peer Teaching Observation}, 2023--2024. %Wendy Wang
\item \textit{Department of Government Peer Teaching Observation}, 2022--2023.
\item \textit{Department of Government Gender and Politics (Senior) Search Committee}, 2023--2024.
\item \textit{Department of Government Executive Committee}, 2022--2023.
\item \textit{Government Department Graduate Annual Review Committee}, AY 2022--2023. 
\item \textit{Department of Government Executive Committee}, 2020--2021.
\item \textit{Department of Government Diversity Task Force}, 2020--2021.
\item \textit{Senior IR Faculty Search Committee}, 2018--2019.
\item \textit{Government Department Graduate Financial Aid Committee}, AY 2018--2019. 
\item \textit{Department Workshop on Innovations in Teaching, Organizer}, 2018--2020.
\item \textit{Committee on Women in Political Science}, 2015--present.
\item \textit{Executive Committee, Government Department}, 2015--2018.
\item \textit{UT Department of Government, Public Policy Job Search Committee}, Spring 2017
\item \textit{Organizer International Relations Workshop}, UT-Austin, AY 2014-2015.
\item \textit{Co-Organizer Government Department Experiments Workshop}, UT-Austin, Spring 2013; AY 2014-2015.
\item \textit{Government Department Graduate Financial Aid Committee (elected by graduate students)}, UT-Austin, AY 2014--2015. 
\item \textit{Government Department Graduate Admissions Committee}, UT-Austin, AY 2012--2013; AY 2013--2014.
\item \textit{Faculty Research Group Coordinator}, BYU, Spring Term 2012.
\item \textit{Curriculum Committee}, BYU, AY 2007--2010; 2011--2012.
\item \textit{Academic Life Committee}, BYU, AY 2009--2010; 2011--2012.
\item \textit{Speaker at numerous BYU student honor society and club meetings}, BYU, 2007--2012.

\end{itemize}

\subsection*{Graduate Training}
\begin{itemize}\setlength{\itemsep}{1pt}

\item \emph{Placement}
\\ \indent \textit{-Olgahan \c{C}at, Brown University Visiting Assistant Professor, 2025 (Chair)}
\\ \indent \textit{-Alex Wais, University of Stockholm Postdoc, 2025 (Chair)}
\\ \indent \textit{-Jiseon Chang, Tecnol\'ogico de Monterrey, Previously Princeton Niehaus Postdoc, 2024 (Chair)}
\\ \indent \textit{-Xin Nong, Hitotsubashi University, 2024 (Chair)}
\\ \indent \textit{-Kevin Galambos, Rhodes College, 2024 (Committee)}
\\ \indent \textit{-Michael Denly, Texas A\&M Bush School, 2023 (Chair)}
\\ \indent \textit{-Hans-Inge Lango, The Carter Center, 2021 (Committee)}
\\ \indent \textit{-Megan Farrell, FEMA, 2020 (Chair)}
\\ \indent \textit{-Kyosuke Kikuta, JETRO-IDE (Osaka University), 2019 (Chair)}
\\ \indent \textit{-Josiah Marineau, University of North Carolina at Pembroke, 2016 (Chair) }
%\\ \indent \textit{-Daniel Strandow, Swedish Government \& Private Consulting, 2014 (Co-chair) }
\\ \indent \textit{-Nathalia Sandoval, FGV RI, Brazil, 2020 (Committee)}
\\ \indent \textit{-Calla Hummel, University of Miami, Tenure track, 2017 (Committee)}
\\ \indent \textit{-Todd Smith, University of Nevada at Reno, Tenure track, 2015 (Committee)}
\\ \indent \textit{-Daniel McCormack, University of Pennsylvania, Post-doc, 2015 (Committee)}
\\ \indent \textit{-Huseyin Alpetkin, Istanbul Sehir University, 2014 (Committee)}
\\ \indent \textit{-Henry Pascoe, IE University, 2016 (Committee)}


\item \emph{Phd Dissertation Chair}
\\ \indent \textit{-Kylie Smith, Government Department (Chair; Ongoing)}
\\ \indent \textit{-Chukwuemeka Ohajionu, Government Department (Chair; Ongoing)}
% \\ \indent \textit{-Gaeun Jung, Government Department (Chair; Ongoing)}
% \\ \indent \textit{-ChangHa Kim, Government Department (Chair; Ongoing)}

\item \emph{Phd Dissertation Committees}
\\ \indent \textit{-Danny Cowser, Government Department}
\\ \indent \textit{-Heartlee Harman, Government Department}
\\ \indent \textit{-Joseph Amoah, Government Department}

%\item \emph{Masters Thesis Committees}, University of Texas at Austin, 2012--
%\\ \indent \textit{-XX, LBJ Public Policy School} 

\end{itemize}


\subsection*{Miscellaneous Affiliations, Training, and Talks} 
\begin{itemize}
\item \textit{UNESCO Inclusive Policy Lab Expert}, June 2021--
\item \textit{Guest Researcher Uppsala University Department of Peace and Conflict Research}, Uppsala, Sweden, May 2010, June 2011
\item \textit{Academic Fellows Program for the Study of Terrorism}, Tel Aviv, Israel (Foundation for the Defense of Democracies), June 2009
\item \textit{Designing, Conducting, and Analyzing Field Experiments}, Yale University (ICPSR workshop), July 2008
\item \textit{Summer Workshop on Teaching about Terrorism}, University of Oklahoma, June 2008
\item \textit{APSA Short Course on Agent-Based Modeling}, Philadelphia, PA, Sept 2006
\item \textit{Graduate Workshop in Computational Social Sciences and Complexity}, Santa Fe Institute, Santa Fe New Mexico, July 2006
\item \textit{Merriam Workshop in Math Modeling}, Merriam Lab for Political Research, UIUC, January 2006
\item \textit{Junior Master Class}, Merriam Lab for Political Research, UIUC, Oct. 2004 \& Sept. 2005
\item \textit{Repast Training Seminar}, Agent 2004 Conference,  Argonne National Laboratory, Chicago, October 2004
\end{itemize}


\section*{RESEARCH SKILLS}
\subsection*{Modeling and Technical Skills} \setlength{\itemsep}{1pt}
\begin{itemize}
\item Experiments; Computational modeling; Applied statistics; Geographic information systems; Interviews; Impact Evaluation; External validity.
\item Proficient in R, Stata, Matlab, and \LaTeX\ --- Familiar with ArcGIS, RATS, SPSS, and Mathematica.
\end{itemize}

\subsection*{International and Language Skills}

%add europe trip countries and any others missing

\begin{itemize}\setlength{\itemsep}{1pt}
\item Reading, Writing, Speaking:
    \begin{itemize} \setlength{\itemsep}{1pt}
    \item Russian: proficient reading, writing, \& speaking.
    \item Serbo-Croatian: basic reading \& writing.
    \item Spanish: basic reading \& writing.
    \end{itemize}
\item Field Research and International Experience: \setlength{\itemsep}{1pt}
    \begin{itemize}
    \item Bahamas: Nassau; January 2020; January 2022; January 2023; January 2024; January 2025; January 2026
    \item France: November 2018; April--June 2025
    \item Morocco: May--June 2025
    \item Ethiopia: Addis Abbaba; April 2020
    \item Tanzania: Dar es Salaam, Arusha; July 2019
    \item Colombia: Bogota, Monteria, Valencia, Cali, Miranda, Florida, Medellin, Icononzo, Chaparral, Planeta Rica, Tierralta, Covenas; November 2014; August 2015; September 2015; March 2016; July 2016; May 2017; October 2017; July 2018; May 2019; July 2019; January 2020
    \item Uganda: Kampala, Gulu; June 2010; January 2011; May 2011; June--July 2012; June--July 2013; June 2015; May 2018; July 2019
    \item Kenya: Nairobi; December 2010; October 2013; May 2015; October 2016; January 2017; July 2019
    \item Sudan: Khartoum; January 2016
    \item South Sudan: Juba; January 2016
    \item Democratic Republic of the Congo: Kinshasa, Goma; May 2015
    \item Rwanda: Kigali; July 2012; Kigali, July 2013; June 2015; January 2016.
    \item Germany: Munich; May 2012
    \item Senegal: Dakar; January 2012
    \item Malawi: Lilongwe; January 2011
    \item Sweden: Uppsala; May 2010; June 2011; October 2013
    \item South Africa: East London, Johannesburg, Durban, Cape Town; November 2008; July 2009; April 2010; March 2016
    \item England: Cambridge; November 2019, April 2018; Oxford, November 2019, March 2010; London, November 2019, April 2017, December 2015. 
    \item Switzerland: Geneva; January 2013
    \item Israel: Tel Aviv, Jerusalem; June 2009
    \item Guatemala: Antigua, Chimaltenango, Panajachel; May 2009.
    \item Russia: Yekaterinburg, Ufa, Cheliabinsk, Perm; October 1995--September 1997
    \item Mexico: Toluca, Mexico City, June--July 1993
    \end{itemize}
\end{itemize}


\section*{REFERENCES}

Available upon request


\end {document}





